\documentclass{article}
\iffalse
This file is protected by Copyright. Please refer to the COPYRIGHT file
distributed with this source distribution.

This file is part of OpenCPI <http://www.opencpi.org>

OpenCPI is free software: you can redistribute it and/or modify it under the
terms of the GNU Lesser General Public License as published by the Free Software
Foundation, either version 3 of the License, or (at your option) any later
version.

OpenCPI is distributed in the hope that it will be useful, but WITHOUT ANY
WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A
PARTICULAR PURPOSE. See the GNU Lesser General Public License for more details.

You should have received a copy of the GNU Lesser General Public License along
with this program. If not, see <http://www.gnu.org/licenses/>.
\fi

\usepackage{textcomp}
\usepackage{ragged2e}
\usepackage{amsmath}
\author{} % Force author to be blank
%----------------------------------------------------------------------------------------
% Paper size, orientation and margins
%----------------------------------------------------------------------------------------
\usepackage{geometry}
\geometry{
	letterpaper,			% paper type
	portrait,				% text direction
	left=.75in,				% left margin
	top=.75in,				% top margin
	right=.75in,			% right margin
	bottom=.75in			% bottom margin
 }
%----------------------------------------------------------------------------------------
% Header/Footer
%----------------------------------------------------------------------------------------
\usepackage{fancyhdr} \pagestyle{fancy} % required for fancy headers
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}
\rhead{\small{ANGRYVIPER Team}}
%----------------------------------------------------------------------------------------
% Appendix packages
%----------------------------------------------------------------------------------------
\usepackage[toc,page]{appendix}
%----------------------------------------------------------------------------------------
% Defined Commands & Renamed Commands
%----------------------------------------------------------------------------------------
\renewcommand{\contentsname}{Table of Contents}
\renewcommand{\listfigurename}{List of Figures}
\renewcommand{\listtablename}{List of Tables}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1}} % To do notes
\newcommand{\code}[1]{\texttt{#1}} % For inline code snippet or command line
%----------------------------------------------------------------------------------------
% Various pacakges
%----------------------------------------------------------------------------------------
\usepackage{hyperref} % for linking urls and lists
\usepackage{graphicx} % for including pictures by file
\usepackage{listings} % for coding language styles
\usepackage{rotating} % for sideways table
\usepackage{pifont}   % for sideways table
\usepackage{pdflscape} % for landscape view
\usepackage{longtable}
%----------------------------------------------------------------------------------------
% Table packages
%----------------------------------------------------------------------------------------
\usepackage{longtable} % for long possibly multi-page tables
\usepackage{tabularx} % c=center,l=left,r=right,X=fill
\usepackage{float}
\floatstyle{plaintop}
\usepackage[tableposition=top]{caption}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
%----------------------------------------------------------------------------------------
% Block Diagram / FSM Drawings
%----------------------------------------------------------------------------------------
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,fit,positioning}
\usetikzlibrary{automata} % used for the fsm
%----------------------------------------------------------------------------------------
% Colors Used
%----------------------------------------------------------------------------------------
\usepackage{colortbl}
\definecolor{blue}{rgb}{.7,.8,.9}
\definecolor{ceruleanblue}{rgb}{0.16, 0.32, 0.75}
\definecolor{drkgreen}{rgb}{0,0.6,0}
\definecolor{deepmagenta}{rgb}{0.8, 0.0, 0.8}
\definecolor{cyan}{rgb}{0.0,0.6,0.6}
\definecolor{maroon}{rgb}{0.5,0,0}
%----------------------------------------------------------------------------------------
% Update the docTitle and docVersion per document
%----------------------------------------------------------------------------------------
\def\docTitle{Component Data Sheet}
\def\docVersion{1.1}
%----------------------------------------------------------------------------------------
\date{Version \docVersion} % Force date to be blank and override date with version
\title{\docTitle}
\lhead{\small{\docTitle}}

% do not delete this line, it is used by the auto gen script to insert latex code
\def\comp{data\_src}
\edef\ecomp{data_src}
%GEN_COMPLC_NAME
\def\Comp{TEMP}
% do not delete this line, it is used by the auto gen script to insert latex code
\def\Comp{Data\_Src }
%GEN_COMPUC_NAME
\graphicspath{ {figures/} }

\begin{document}

\section*{Summary - \Comp}
\begin{tabular}{|c|M{13.5cm}|}
	\hline
	\rowcolor{blue}
	                  &                                                                                \\
	\hline
	Name              & \comp                                                                          \\
	\hline
	Worker Type       & Application                                                                    \\
	\hline
	Version           &  v1.4                                                                         \\
	\hline
	Release Date      & October 2018 \\
	\hline
	Component Library & ocpi.assets.misc\_comps \\
	\hline
	Workers           & \comp.hdl \\
	\hline
	Tested Platforms  & zed, matchstiq\_z1, e3xx, alst4, ml605, xsim \\
	\hline
\end{tabular}

\section*{Functionality}
\begin{flushleft}
\justify
  \Comp selects one \verb+DATA_BIT_WIDTH_p+ bits-wide data bus from multiple data generation sources, packs the \verb+DATA_BIT_WIDTH_p+ bits in bit-forward order in the least significant bits of the I data bus and bit-reverse order in the most significant bits of the Q data bus, and outputs that I/Q bus to the \verb+out+ port. The \verb+DATA_BIT_WIDTH_p+ bits-wide data sources are:
  \begin{itemize}
  \item a unsigned counter,
  \item a walking ones bus (e.g. b'100 \textrightarrow b'010 \textrightarrow b'001 \textrightarrow b'100 \textrightarrow etc),
  \item a Linear Feedback Shift Register (LFSR),
  \item and a property-driven fixed value.
  \end{itemize}
  The bitwidth common to all data source buses is parameterized. In the case that the data source bus width is less than the iqstream I/Q widths of 16 bits, the bus is packed into the most significant bits of I and Q. This aids in data alignment when this component is connected directly to a DAC device worker, which commonly takes the DAC bitwidth-most significant bits of I and Q from an iqstream input port for its data transmission. \\ \medskip
  This component includes a property-driven setting which can optionally disable the output port once a specified number of samples have been sent. This component can also be parameterized to send a Zero-Length Message (ZLM) once the output port is disabled.
\end{flushleft}

\section*{Worker Implementation Details}
\begin{flushleft}
\subsection*{\comp.hdl}
\justify
  In keeping with good data flow control practices, backpressure from the output port will suspend the advancement of each data generation source. The \verb+ZLM_WHEN_NUM_SAMPLES_REACHED_p+ parameter, when having a value of true, forces the worker to send a single ZLM when the output port has been disabled (i.e. when the \verb+num_samples+ property has a value of more than 1 and \verb+num_samples+ amount of samples have been sent out the output port). This is useful for allowing applications which use this worker to terminate once this worker's output port is disabled.
\end{flushleft}

\section*{Block Diagrams}
\subsection*{\comp.hdl - Top level}
\begin{center}
  \begin{tikzpicture}[% List of styles applied to all, to override specify on a case-by-case
      every node/.style={
        align=center,     % use this so that the "\\" for line break works
        minimum size=2cm  % creates space above and below text in rectangle
      },
      every edge/.style={draw,thick}
    ]
    \node[rectangle,ultra thick,draw=black,fill=blue](R2){\verb+DATA_BIT_WIDTH_p,+ \\ \verb+LFSR_POLYNOMIAL_p,+ \\ \verb+LFSR_SEED_p,+ \\ \verb+ZLM_WHEN_NUM_SAMPLES_REACHED_p+, \\ \verb+ODATA_WIDTH_p+ \\ \\ \Comp \\ };
    \node[rectangle,draw=white,fill=white](R4)[right= of R2]{``out'' \\ iqstream\_protocol \\ (complex signed Q0.15 samples)};
    \node[rectangle,draw=white,fill=white](R5)[above= of R2]{\verb+LFSR_bit_reverse+, \\ \verb+mask_I,+ \\ \verb+mask_Q+};
    \path[->]
    (R2)edge [] node [] {} (R4)
    (R2)edge [] node [] {} (R5)
    (R5)edge [] node [] {} (R2)
    ;
  \end{tikzpicture}
\end{center}\pagebreak

\section*{Source Dependencies}
\subsection*{\comp.hdl}
\begin{itemize}
  \item assets/components/misc\_comps/\comp.hdl/\comp.vhd
  \item assets/components/misc\_comps/\comp.hdl/out\_port\_inject\_zlm.vhd
  \item assets/components/misc\_comps/\comp.hdl/set\_clr.vhd
  \item assets/primitives/misc\_prims/lfsr/src/lfsr.vhd
\end{itemize}


\begin{landscape}
	\section*{Component Spec Properties}
	\begin{scriptsize}
% do not delete this line, it is used by the auto gen script to insert latex code
\begin{longtable}{|p{5.5cm}|p{1.25cm}|p{2cm}|p{2.75cm}|p{1.5cm}|p{1.5cm}|p{1cm}|p{5.25cm}|}
\hline
\rowcolor{blue}
Name                 & Type   & SequenceLength & ArrayDimensions & Accessibility       & Valid Range & Default & Usage
\\
\hline
DATA\_BIT\_WIDTH\_p & ushort  & - & - & Parameter & -  &16 & Determines the width of the buses for each of the I and Q data generation memory elements - if less than 16, the most significant \verb+DATA_BIT_WIDTH_p+ bits of I and Q on the out port will be filled. Value is expect to be less than or equal to 16.
\\
\hline
LFSR\_POLYNOMIAL\_p & bool  & - & DATA\_BIT\_WIDTH\_p & Parameter & -  &0 & E.g., a value of 1,1,0,1 would correspond to an LFSR polynomial of \begin{equation*}x^4 + x^3 + (0*x^2) + x^1 + 1\end{equation*} (+1 is always implied regardless of value).
\\
\hline
LFSR\_SEED\_p & bool  & - & DATA\_BIT\_WIDTH\_p & Parameter & -  &0 & Out-of-reset value of the Linear Feedback Shift Register (only affects output data in LFSR mode). This value should never be all zeros, which would cause the register to always have a value of all zeros regardless of polynomial value.
\\
\hline
ZLM\_WHEN\_NUM\_SAMPLES\_REACHED\_p & bool  & - & - & Parameter & -  &false & When value is true and \verb+num_samples+ property value is not -1, worker will generate Zero-Length-Message after \verb+num_samples+ amount of samples have been sent out the output port. Note this functionality is independent of the value of the \verb+enable+ property.

\\
\hline
messageSize\_bytes & ulong  & - & - & Readable, Initial & -  &4096 & Message size in bytes. When the value of (\verb+num_samples+ * num bytes per sample) is less than this property's value, the value of (\verb+num_samples+ * num bytes per sample) is used as the message size.
\\
\hline
num\_samples & long  & - & - & Readable, Writeable & -  &-1 & Maximum number of samples which will be sent out of the output port once out of reset. Note that samples are only sent when the \verb+enable+ property has a value of true. When the value of this property is -1, samples will be sent indefinitely (obeying backpressure from the connected worker, of course).
\\
\hline
fixed\_value & bool  & - & DATA\_BIT\_WIDTH\_p & Readable, Writeable & -  &0x5a5a & The value of this property will be used for I (and the bit-reversed version of this value will be used for Q) to send to the output port when the \verb+mode+ property's value is 'fixed'.
Array index 0 corresponds to the 15th (most significant) I bit and the 16-\verb+DATA_BIT_WIDTH_p Q+ bit of the out port,
array index 1 corresponds to the 14th (next-to-most significant) I bit and the 15-\verb+DATA_BIT_WIDTH_p+ Q bit of the out port, etc...
\\
\hline
mode & enum  & - & - & Readable, Writeable & count,walking, LFSR,fixed  &count & Counter, walking ones, Linear Feedback Shift Register, or fixed value. The counter is unsigned.
\\
\hline
enable & bool  & - & - & Readable, Writeable & -  &true & When the worker is not in reset, this property must have a value of true for the data to be sent to the output. Note that this property has no effect on the ZLM operation (see \verb+ZLM_WHEN_NUM_SAMPLES_REACHED_p+ parameter property).
\\
\hline
LFSR\_bit\_reverse & bool  & - & - & Readable, Writeable & -  &true & Used to determine the LFSR shift direction. When true, the \verb+DATA_BIT_WIDTH_p+-bits wide LFSR will be reversed for both I and Q.
\\
\hline
mask\_I & ushort & - & - & Readable, Writable & -  &0xffff & I data will be bitwise anded with this mask before being sent to out port.
\\
\hline
mask\_Q & ushort & - & - & Readable, Writable & -  &0xffff & Q data will be bitwise anded with this mask before being sent to out port.
\\
\hline
\end{longtable}
%GEN_SPEC_TABLE
	\end{scriptsize}

	\section*{Worker Properties}
	\subsection*{\comp.hdl}
	\begin{scriptsize}
% do not delete this line, it is used by the auto gen script to insert latex code
%GEN_WORKER_TABLE
\begin{longtable}{|p{5.5cm}|p{1.25cm}|p{2cm}|p{2.75cm}|p{1.5cm}|p{1.5cm}|p{1cm}|p{5.25cm}|}
\hline
\rowcolor{blue}
Name                 & Type   & SequenceLength & ArrayDimensions & Accessibility       & Valid Range & Default & Usage
\\
\hline
ODATA\_WIDTH\_p & ushort  & - & - & Parameter & -  &32 & Value is assigned to the out port's data width.
\\
\hline
\end{longtable}

	\end{scriptsize}

	\section*{Component Ports}
	\begin{scriptsize}
% do not delete this line, it is used by the auto gen script to insert latex code
\begin{tabular}{|M{2cm}|M{1.5cm}|M{4cm}|c|c|M{9cm}|}
\hline
\rowcolor{blue}
Name & Producer & Protocol & Optional & Advanced & Usage
\\
\hline
out & true & iqstream\_protocol& False & ZeroLengthMessages=true & Complex signed samples (Q0.15 I, Q0.15 Q). This port generates data while obeying backpressure. Data is no longer sent to this port when either the enable property has a value of false or when the \verb+num_samples+ property has a value of greater than 0 and \verb+num_samples+ amount of samples have been sent out this port.\\
\hline
\end{tabular}
%GEN_PORT_TABLE
	\end{scriptsize}

	\section*{Worker Interfaces}
	\subsection*{\comp.hdl}
	\begin{scriptsize}
\begin{tabular}{|M{2cm}|M{1.5cm}|M{4cm}|c|M{12cm}|}
\hline
\rowcolor{blue}
Type & Name & DataWidth & Advanced & Usage
\\
\hline
StreamInterface & out & 32 & - & -\\
\hline
\end{tabular}
%GEN_INTERFACE_TABLE
	\end{scriptsize}
\end{landscape}

\section*{Control Timing and Signals}
\subsection*{\comp.hdl}
\begin{flushleft}
  The \Comp worker uses the clock from the Control Plane and standard Control Plane signals.
\end{flushleft}

\begin{landscape}
\section*{Worker Configuration Parameters}
\subsubsection*{\comp.hdl}
\input{../../\ecomp.hdl/configurations.inc}
\section*{Performance and Resource Utilization}
\subsubsection*{\comp.hdl}
\input{../../\ecomp.hdl/utilization.inc}
\end{landscape}

\section*{Test and Verification}
\begin{flushleft}
\justify
For verification, multiple test are run with varying values for the \verb+num_samples+ property for each of the available data source modes. The output file is checked for expected length and data contents, with the data content check being specific to the given data source mode.
\end{flushleft}
\end{document}
