%TODO: Use LaTeX_Header
\documentclass{article}
\iffalse
This file is protected by Copyright. Please refer to the COPYRIGHT file
distributed with this source distribution.

This file is part of OpenCPI <http://www.opencpi.org>

OpenCPI is free software: you can redistribute it and/or modify it under the
terms of the GNU Lesser General Public License as published by the Free Software
Foundation, either version 3 of the License, or (at your option) any later
version.

OpenCPI is distributed in the hope that it will be useful, but WITHOUT ANY
WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A
PARTICULAR PURPOSE. See the GNU Lesser General Public License for more details.

You should have received a copy of the GNU Lesser General Public License along
with this program. If not, see <http://www.gnu.org/licenses/>.
\fi

\author{} % Force author to be blank
%----------------------------------------------------------------------------------------
% Paper size, orientation and margins
%----------------------------------------------------------------------------------------
\usepackage{geometry}
\geometry{
  letterpaper,      % paper type
  portrait,       % text direction
  left=.75in,       % left margin
  top=.75in,        % top margin
  right=.75in,      % right margin
  bottom=.75in      % bottom margin
 }
%----------------------------------------------------------------------------------------
% Header/Footer
%----------------------------------------------------------------------------------------
\usepackage{fancyhdr} \pagestyle{fancy} % required for fancy headers
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}
\newcommand{\terminaloutput}[1]{\texttt{#1}}
\rhead{\small{ANGRYVIPER Team}}
%----------------------------------------------------------------------------------------
% Appendix packages
%----------------------------------------------------------------------------------------
\usepackage[toc,page]{appendix}
%----------------------------------------------------------------------------------------
% Defined Commands & Renamed Commands
%----------------------------------------------------------------------------------------
\renewcommand{\contentsname}{Table of Contents}
\renewcommand{\listfigurename}{List of Figures}
\renewcommand{\listtablename}{List of Tables}
%----------------------------------------------------------------------------------------
% Various pacakges
%----------------------------------------------------------------------------------------
\usepackage{hyperref} % for linking urls and lists
\usepackage{graphicx} % for including pictures by file
\usepackage{listings} % for coding language styles
\usepackage{rotating} % for sideways table
\usepackage{pifont}   % for sideways table
\usepackage{pdflscape} % for landscape view
\usepackage{longtable}
%----------------------------------------------------------------------------------------
% Table packages
%----------------------------------------------------------------------------------------
\usepackage{longtable} % for long possibly multi-page tables
\usepackage{tabularx} % c=center,l=left,r=right,X=fill
\usepackage{float}
\floatstyle{plaintop}
\usepackage[tableposition=top]{caption}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
%----------------------------------------------------------------------------------------
% Block Diagram / FSM Drawings
%----------------------------------------------------------------------------------------
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,fit,positioning}
\usetikzlibrary{automata} % used for the fsm
\usetikzlibrary{calc} % For duplicating clients
\usepgfmodule{oo} % To define a client box
%----------------------------------------------------------------------------------------
% Colors Used
%----------------------------------------------------------------------------------------
\usepackage{colortbl}
\definecolor{blue}{rgb}{.7,.8,.9}
\definecolor{ceruleanblue}{rgb}{0.16, 0.32, 0.75}
\definecolor{drkgreen}{rgb}{0,0.6,0}
\definecolor{deepmagenta}{rgb}{0.8, 0.0, 0.8}
\definecolor{cyan}{rgb}{0.0,0.6,0.6}
\definecolor{maroon}{rgb}{0.5,0,0}
\usepackage{multirow}
%----------------------------------------------------------------------------------------
% Update the docTitle and docVersion per document
%----------------------------------------------------------------------------------------
\def\docTitle{Component Data Sheet}
\def\docVersion{1.5}
%----------------------------------------------------------------------------------------
\date{Version \docVersion} % Force date to be blank and override date with version
\title{\docTitle}
\lhead{\small{\docTitle}}

\def\snippetpath{../../../../../../doc/av/tex/snippets}
\input{\snippetpath/includes}

\def\comp{ad9361\_config}
\edef\ecomp{ad9361_config}
\def\Comp{AD9361 Config}
\graphicspath{ {figures/} }

\begin{document}

\section*{Summary - \Comp}
\begin{tabular}{|c|M{13.5cm}|}
  \hline
  \rowcolor{blue}
                    &                  \\
  \hline
  Name              & \comp            \\
  \hline
  Worker Type       & Device           \\
  \hline
  Version           & v\docVersion   \\
  \hline
  Release Date      & 9/2018         \\
  \hline
  Component Library & ocpi.assets.devices     \\
  \hline
  Workers           & \comp.hdl        \\
  \hline
	Tested Platforms  &
\begin{itemize}
  \item Agilent Zedboard/Analog Devices FMCOMMS2 (Vivado only)
  \item Agilent Zedboard/Analog Devices FMCOMMS3 (Vivado only)
  \item x86/Xilinx ML605/Analog Devices FMCOMMS2
  \item x86/Xilinx ML605/Analog Devices FMCOMMS3
  \item Ettus E310 (Vivado only)
\end{itemize} \\
  \hline
\end{tabular}

\tableofcontents

\section{Functionality}
  The \Comp{} is a subdevice worker which provides an entry point to the major functionality of the AD9361 IC\cite{ad9361}. This includes both SPI bus functionality for intercommunication with the AD9361 register map as well as additional command/control between the software and the FPGA. Note that, while the register address decoding is performed within this worker, the SPI state machine itself is implemented in one or more separate, platform-specific or card-specific subdevice workers\footnote{For an example, see \cite{spi_comp_datasheet}}. This worker's register map provides an API for integrating with Analog Devices's No-OS software\cite{no_os}. This integration is implemented in \cite{config_proxy_comp_datasheet}.

\section{Worker Implementation Details}
\subsection{\comp.hdl}
The AD9361 register map is realized via a rawprops port whose communication is forwarded on to a SPI subdevice worker. The register map is implemented via the Component Spec properties for this worker, all of which correspond with the AD9361 register map specified in \cite{adi_ug671}. This worker also operates itself as subdevice which 1) conveys build-time information from the ad9361\_adc\_sub.hdl and ad9361\_dac\_sub.hdl device workers up to the processor via properties and 2) conveys processor-known assumptions about the AD9361 multichannel configuration to the ad9361\_adc\_sub.hdl and ad9361\_dac\_sub.hdl workers.

\section{Block Diagrams}
\subsection{Top level}
\makeatletter
\newcommand{\gettikzxy}[3]{%
  \tikz@scan@one@point\pgfutil@firstofone#1\relax
  \edef#2{\the\pgf@x}%
  \edef#3{\the\pgf@y}%
}
\makeatother
\pgfooclass{clientbox}{ % This is the class clientbox
    \method clientbox() { % The clientbox
    }
    \method apply(#1,#2,#3,#4) { % Causes the clientbox to be shown at coordinate (#1,#2) and named #3
        \node[rectangle,draw=white,fill=white] at (#1,#2) (#3) {#4};
    }
}
\pgfoonew \myclient=new clientbox()
\begin{center}
  \begin{tikzpicture}[% List of styles applied to all, to override specify on a case-by-case
      every node/.style={
        align=center,      % use this so that the "\\" for line break works
        minimum size=1cm,  % creates space above and below text in rectangle
      },
      every edge/.style={draw,thick}
    ]
    \node[rectangle,ultra thick,draw=black,fill=blue,minimum size=2cm,minimum width=15cm](R1){Parameter Properties: \verb+pin_control_p+ \\ \Comp};
    \node[rectangle,draw=white,fill=white](R4)[above= of R1]{ };
    \node[rectangle,draw=white,fill=white](placeholder)[above= of R1] { Non-parameter \\ Properties:\\ \verb+other_present+ \\ \verb+force_reset+ \\ \verb+qadc0_is_present+ \\ \verb+qadc1_is_present+ \\ \verb+qdac0_is_present+ \\ \verb+qdac1_is_present+ \\ \verb+rx_frame_usage+ \\ \verb+data_bus_index_direction+ \\ \verb+data_clk_is_inverted+ \\ \verb+rx_frame_is_inverted+ \\ \verb+p0_p1_are_swapped+ \\ \verb+iostandard+ \\ \verb+port_config+ \verb+duplex_config+ \\ \verb+data_rate_config+ \\ \verb+data_configs_are_valid+ \\ \verb+config_is_two_r+ \\ \verb+config_is_two_t+ \\ \verb+force_two_r_two_t_timing+ \\ \verb+Half_Duplex_Mode+ \\ \verb+ENSM_Pin_Control+ \\ \verb+Level_Mode+ \\ \verb+FDD_External_Control_Enable+ \\ \verb+ENABLE_force_set+ \\ \verb+TXNRX_force_set+ \\ (ad9361 register set - see Appendix \ref{appendix:properties}) };
    \path[->]
  (R1)edge [] node [] {} (R4)
  (R4)edge [] node [] {} (R1)
    ;
    \gettikzxy{(placeholder)}{\rx}{\ry}
    \myclient.apply(\rx - 180,\ry-290,C1, ``dev\_force\_spi\_reset'' \\ dev signal port \texttt{(}see \\ AD9361\_SPI.pdf\texttt{)} );
    \path[->]($(R1.south) + (-180 pt,0)$) edge [] node [] {} (C1);
    \myclient.apply(\rx - 60,\ry-290,C1, ``rawprops'' \\ rawprop \texttt{(}see \\ AD9361\_SPI.pdf\texttt{)} );
    \path[->]($(R1.south) + (-60 pt,0)$) edge [] node [] {} (C1);
    \myclient.apply(\rx + 60,\ry-290,C1, ``dev\_cfg\_data\_port'' \\ dev signal port \texttt{(}see \\ AD9361\_DATA\_SUB.pdf\texttt{)} );
    \path[->]($(R1.south) + (60 pt,0)$) edge [] node [] {} (C1);
    \myclient.apply(\rx + 180,\ry-290,C1, ``dev\_txen\_data\_sub'' \\ dev signal port \texttt{(}see \\ AD9361\_DATA\_SUB.pdf\texttt{)} );
    \path[<-]($(R1.south) + (180 pt,0)$) edge [] node [] {} (C1);
	\fontsize{9.5}{12}\selectfont
    \myclient.apply(\rx - 190,\ry,C1, ``dev\_cfg\_data\_rx'' \\ dev signal port \\ sent from \\ ad9361\_adc\_sub.hdl);
    \path[<-]($(R1.north) + (-190 pt,0)$) edge [] node [] {} (C1);
    \myclient.apply(\rx - 108,\ry,C1, ``dev\_cfg\_data''[0] \\ dev signal port \\ sent to \\ ad9361\_adc\_sub.hdl );
    \path[->]($(R1.north) + (-108 pt,0)$) edge [] node [] {} (C1);
    \myclient.apply(\rx + 108,\ry,C1, ``dev\_cfg\_data''[1] \\ dev signal port \\ sent to \\ ad9361\_dac\_sub.hdl );
    \path[->]($(R1.north) + (+108 pt,0)$) edge [] node [] {} (C1);
    \myclient.apply(-\rx + 190,\ry,C1, ``dev\_cfg\_data\_tx'' \\ dev signal port \\ sent from \\ ad9361\_dac\_sub.hdl);
    \path[<-]($(R1.north) + (190 pt,0)$) edge [] node [] {} (C1);
  \end{tikzpicture}
\end{center}

\section{Source Dependencies}
\subsection{\comp.hdl}
\begin{itemize}
  \item assets/hdl/devices/\comp.hdl/\comp.vhd
  \item assets/hdl/devices/ad9361\_config.hdl/signals.vhd
\end{itemize}
\begin{landscape}
  \section{Component Spec Properties}
  See Appendix \ref{appendix:properties}.

  \section{Component Ports}
  \begin{scriptsize}
    \begin{tabular}{|p{2cm}|p{1.5cm}|p{4cm}|p{1.5cm}|p{1.5cm}|p{11.29cm}|}
      \hline
      \rowcolor{blue}
      Name & Producer & Protocol           & Optional & Advanced & Usage                  \\
      \hline
      -    & -        & -                  & -        & -        & - \\
      \hline
    \end{tabular}
  \end{scriptsize}

  \section{Worker Properties}
  \begin{scriptsize}
    \begin{tabular}{|p{3.75cm}|p{1.25cm}|p{2cm}|p{2.75cm}|p{1.5cm}|p{1.5cm}|p{1cm}|p{7.17cm}|}
      \hline
      \rowcolor{blue}
      Name               & Type & SequenceLength & ArrayDimensions & Accessibility      & Valid Range & Default & Usage                                                                               \\
      \hline
      pin\_control\_p & Bool & - & - & Parameter & Standard & - & Whether RX/TX powerdown via pin control is possible. \\
      \hline
    \end{tabular}
  \end{scriptsize}

  \section{Worker Interfaces}
  \subsection{\comp.hdl}
  \begin{scriptsize}
    \begin{longtable}{|p{1.75cm}|p{3.25cm}|p{18.10cm}|}
    \hline
    \rowcolor{blue}
    Type              & Name                    & Master    \\
    \hline
    Rawprop           & rawprops                & True      \\
    \hline
    \end{longtable}
  \pagebreak
\begin{longtable}{|p{1.75cm}|p{2.25cm}|p{1.25cm}|p{1.25cm}|p{0.95cm}|p{3cm}|p{1.4cm}|p{0.9cm}|p{7.25cm}|}
			\hline
			\rowcolor{blue}
			Type                       & Name                            & Count & Optional & Master                & Signal                & Direction                  & Width                    & Description                                                                                                                  \\
			\hline
			\multirow{2}{*}{DevSignal} & \multirow{2}{*}{dev\_force\_spi\_reset} & \multirow{2}{*}{1} & \multirow{2}{*}{False} & \multirow{2}{*}{True} & force\_reset & Output & 1 & Used to force AD9361 RESETB pin, which is active-low, to logic 0. \\
			\hline
			\multirow{5}{*}{DevSignal} & \multirow{5}{*}{dev\_cfg\_data\_port} & \multirow{5}{*}{1} & \multirow{5}{*}{False} & \multirow{5}{*}{True} & iostandard\_is\_lvds & Input     & 1      & Value is 1 if the buildtime configuration was for the LVDS mode and 0 otherwise. \\
			\cline{6-9}
			                           &                                 &                    &                       &                        & p0\_p1\_are\_swapped & Input               &                           1 & Value is 1 if the buildtime configuration was with the AD9361 P0 and P1 data port roles inverted and 0 otherwise. \\
			\hline
			\multirow{38}{*}{DevSignal} & \multirow{38}{*}{dev\_cfg\_data} & \multirow{38}{*}{2} & \multirow{38}{*}{True} & \multirow{38}{*}{False} & config\_is\_two\_r &Input& 1      & Some data port configurations (such as LVDS) require the TX bus to use 2R2T timing if either 2 TX or 2 RX channels are used. For example, if using LVDS and this has a value of 1, 2R2T timing will be forced. \\
			\cline{6-9}
			&             &        &     &      & ch0\_handler\_is\_present &Output & 1      & Value is 1 if the dev\_data\_ch0 dev signal is connected to a worker (that ``handles'' the data) and 0 otherwise. This is expected to be hardcoded at buildtime. \\
			\cline{6-9}
			&             &        &     &      & ch1\_handler\_is\_present &Output & 1      &  Value is 1 if the dev\_data\_ch1 dev signal is connected to a worker (that ``handles'' the data) and 0 otherwise. This is expected to be hardcoded at buildtime. \\
			\cline{6-9}
			&             &        &     &      & data\_bus\_index\_direction &Output&1      &  Value is 1 if the bus indexing of the P0\_D/P1\_D signals from dev\_data\_from\_pins was reversed before processing. This is expected to be hardcoded at buildtime. \\
			\cline{6-9}
			&             &        &     &      & data\_clk\_is\_inverted     &Output& 1      & Value is 1 if the clock in via dev\_data\_clk was inverted inside this worker before used as an active-edge rising clock. This is expected to be hardcoded at buildtime. \\
			\cline{6-9}
			&             &        &     &      & islvds       & Output     & 1      &  Value is 1 if \verb+DIFFERENTIAL_p+ has a value of true and 0 if \verb+DIFFERENTIAL_p+ has a value of false. Because \verb+DIFFERENTIAL_p+ is a parameter property, this is hardcoded at buildtime.\\
			\cline{6-9}
			&             &        &     &      & isdualport   & Output     & 1      &  Value is 1 if \verb+PORT_CONFIG_p+ has a value of dual and 0 if \verb+PORT_CONFIG_p+ has a value of single. Because \verb+PORT_CONFIG_p+ is a parameter property, this is hardcoded at buildtime.\\
			\cline{6-9}
			&             &        &     &      & isfullduplex & Output     & 1      &  Value is 1 if \verb+DUPLEX_CONFIG_p+ has a value of full\_duplex and 0 if \verb+DUPLEX_CONFIG_p+ has a value of half\_duplex. Because \verb+DUPLEX_CONFIG_p+ is a parameter property, this is hardcoded at buildtime.\\
			\cline{6-9}
			&             &        &     &      & isDDR        & Output     & 1      &  Value is 1 if \verb+DATA_RATE_CONFIG_p+ has a value of DDR and 0 if \verb+DATA_RATE_CONFIG_p+ has a value of SDR. Because \verb+DATA_RATE_CONFIG_p+ is a parameter property, this is hardcoded at buildtime.\\
			\cline{6-9}
			&             &        &     &      & present      & Output     & 1      &  Used to communicate to ad9361\_config.hdl that it should validate the islvds, isdualport, isfullduplex, and isddr signals against similar signals in the ad9361\_adc\_sub.hdl and ad9361\_data\_sub.hdl workers if they are present in the bitstream. This is expected to be hardcoded at buildtime. \\
			\cline{6-9}
			\hline
			\multirow{10}{*}{DevSignal} & \multirow{10}{*}{dev\_cfg\_data\_rx} & \multirow{10}{*}{1} & \multirow{10}{*}{True} & \multirow{10}{*}{False}  & rx\_frame\_usage & Output     & 1      & Value is 1 of worker was built with the assumption that the RX frame operates in its toggle setting and 0 if the assumption was that RX frame has a rising edge on the first sample and then stays high. This value is intended to match that of AD9361 register 0x010 BIT D3\cite{adi_ug671}. This is expected to be hardcoded at buildtime.\\
			\cline{6-9}
			&             &        &     &      & rx\_frame\_is\_inverted &Output& 1 & Rx path-specific data port configuration. Used to tell other workers about the configuration that was enforced when this worker was compiled. This is expected to be hardcoded at buildtime.\\
			\hline
			\multirow{6}{*}{DevSignal} & \multirow{6}{*}{dev\_cfg\_data\_tx} & \multirow{6}{*}{1} & \multirow{6}{*}{True} & \multirow{6}{*}{False}  & config\_is\_two\_t & Input     & 1      & Some data port configurations (such as LVDS) require the TX bus to use 2R2T timing if either 2 TX or 2 RX channels are used. For example, if using LVDS and this has a value of 1, 2R2T timing will be forced.\\
			\cline{6-9}
			&             &        &     &      & force\_two\_r\_two\_t\_timing &Input& 1 & Expected to match value of AD9361 register 0x010 bit D2\cite{adi_ug671}.\\
			\hline
			DevSignal & dev\_rxen\_data\_sub & 1 & False & True  & rxen & Input     & 1      & \\
			\hline
			DevSignal & dev\_txen\_data\_sub & 1 & False & True  & txen & Input     & 1      & \\
			\cline{6-9}
			\hline
		\end{longtable}
	\end{scriptsize}

  \section{Subdevice Connections}
  \begin{scriptsize}
    \begin{tabular}{|p{5cm}|p{5cm}|p{5cm}|p{7.22cm}|}
      \hline
      \rowcolor{blue}
      Supports Worker  & Supports Worker Port & \comp{}.hdl Port   & Index \\
      \hline
      \multirow{2}{*}{ad9361\_adc\_sub} & dev\_cfg\_data       & dev\_cfg\_data     &0 \\
                       & dev\_cfg\_data\_rx   & dev\_cfg\_data\_rx &0 \\
      \hline
      \multirow{2}{*}{ad9361\_dac\_sub} & dev\_cfg\_data       & dev\_cfg\_data     &1 \\
                       & dev\_cfg\_data\_tx   & dev\_cfg\_data\_tx &0 \\
      \hline
    \end{tabular}
  \end{scriptsize}

\end{landscape}

\section{Control Timing and Signals}
The \Comp{} subdevice worker operates in the control plane clock domain. Note that this worker is essentially the central worker that command/control passes through, and no RX or TX data paths flow through this worker.

\begin{landscape}
\section{Performance and Resource Utilization}
\section{Worker Configuration Parameters}
\subsection{\comp.hdl}
\input{../../\ecomp.hdl/configurations.inc}
\subsection{\comp.hdl}
Fmax refers to the maximum allowable clock rate for any registered signal paths within a given clock domain for an FPGA design. Fmax in the table below is specific only to this worker and represents the maximum possible Fmax for any OpenCPI bitstream built with this worker included. Note that the Fmax value for a given clock domain for the final bitstream is often worse than the Fmax specific to this worker, even if this worker is the only one included in the bitstream. \\ \\

%\input{../../\ecomp.hdl/utilization.inc}
\input{utilization_custom.inc}

\end{landscape}

\footnotetext[1]{\label{abc}These measurements were the result of a Vivado timing analysis which was different from the Vivado analysis performed by default for OpenCPI worker builds. For more info see Appendix \ref{appendix:timing}}

\section{Test and Verification}
No standalone unit test currently exists for this worker. However, the test outlined in \cite{dac_comp_datasheet} includes validation of a subset of this worker's functionality (for LVDS only).

\begin{thebibliography}{1}

\bibitem{ad9361} AD9361 Datasheet and Product Info \\
\url{http://www.analog.com/en/products/rf-microwave/integrated-transceivers-transmitters-receivers/wideband-transceivers-ic/ad9361.html}
\bibitem{no_os} AD9361 No-OS Software [Analog Devices Wiki]\\
\url{https://wiki.analog.com/resources/eval/user-guides/ad-fmcomms2-ebz/software/no-os-functions}
\bibitem{adi_ug570} AD9361 Reference Manual UG-570\\
AD9361\_Reference\_Manual\_UG-570.pdf
\bibitem{adi_ug671} AD9361 Register Map Reference Manual UG-671\\
AD9361\_Register\_Map\_Reference\_Manual\_UG-671.pdf
\bibitem{spi_comp_datasheet} AD361 SPI Component Data Sheet \\
\githubioURL{assets/AD9361_SPI.pdf}
\bibitem{dac_comp_datasheet} AD361 DAC Component Data Sheet \\
\githubioURL{assets/AD9361_DAC.pdf}
\bibitem{config_proxy_comp_datasheet} AD361 Config Proxy Component Data Sheet \\
\githubioURL{assets/AD9361_Config_Proxy.pdf}

\end{thebibliography}
\pagebreak
\landscape
\section{Appendix - \comp{}.hdl Properties}
\label{appendix:properties}
\begin{scriptsize}
\input{properties.inc}
\end{scriptsize}
\pagebreak

\section{Appendix - Vivado Timing Analysis}
\label{appendix:timing}
The Vivado timing report that OpenCPI runs for device workers may erroneously report a max delay for a clocking path which should have been ignored. Custom Vivado tcl commands had to be run for this device worker to extract pertinent information from Vivado timing analysis. After building the worker, the following commands were run from the assets project directory (after the Vivado settings64.sh was sourced):
\lstset{language=bash, backgroundcolor=\color{lightgray}, columns=flexible, breaklines=true, prebreak=\textbackslash, basicstyle=\ttfamily, showstringspaces=false,upquote=true, aboveskip=\baselineskip, belowskip=\baselineskip}
\begin{lstlisting}
cd hdl/devices/
vivado -mode tcl
\end{lstlisting}
Then the following commands were run inside the Vivado tcl terminal:
\begin{lstlisting}
open_project ad9361_config.hdl/target-zynq/ad9361_config_rv.xpr
synth_design -part xc7z020clg484-1 -top ad9361_config_rv -mode out_of_context
create_clock -name clk1 -period 0.001 [get_nets {ctl_in[Clk]}]
report_timing -delay_type min_max -sort_by slack -input_pins -group clk1
\end{lstlisting}
The following is the output of the timing report. The Fmax for the control plane clock for this worker is computed as the maximum magnitude slack with a control plane clock of 1 ps plus 2 times the assumed 1 ps control plane clock period (3.135 ns + 0.002 ns = 3.137 ns, 1/3.137 ns = 318.78 MHz).
\fontsize{6}{12}\selectfont
\begin{lstlisting}
Vivado% report_timing -delay_type min_max -sort_by slack -input_pins -group clk1

Timing Report

Slack (VIOLATED) :        -3.135ns  (required time - arrival time)
  Source:                 wci/wci_decode/my_state_r_reg[2]/C
                            (rising edge-triggered cell FDRE clocked by clk1  {rise@0.000ns fall@0.001ns period=0.001ns})
  Destination:            wci/wci_decode/FSM_onehot_my_access_r_reg[0]/CE
                            (rising edge-triggered cell FDSE clocked by clk1  {rise@0.000ns fall@0.001ns period=0.001ns})
  Path Group:             clk1
  Path Type:              Setup (Max at Slow Process Corner)
  Requirement:            0.002ns  (clk1 rise@0.002ns - clk1 rise@0.000ns)
  Data Path Delay:        2.884ns  (logic 0.937ns (32.490%)  route 1.947ns (67.510%))
  Logic Levels:           2  (LUT6=2)
  Clock Path Skew:        -0.049ns (DCD - SCD + CPR)
    Destination Clock Delay (DCD):    0.924ns = ( 0.926 - 0.002 )
    Source Clock Delay      (SCD):    0.973ns
    Clock Pessimism Removal (CPR):    0.000ns
  Clock Uncertainty:      0.035ns  ((TSJ^2 + TIJ^2)^1/2 + DJ) / 2 + PE
    Total System Jitter     (TSJ):    0.071ns
    Total Input Jitter      (TIJ):    0.000ns
    Discrete Jitter          (DJ):    0.000ns
    Phase Error              (PE):    0.000ns

    Location             Delay type                Incr(ns)  Path(ns)    Netlist Resource(s)
  -------------------------------------------------------------------    -------------------
                         (clock clk1 rise edge)       0.000     0.000 r
                                                      0.000     0.000 r  ctl_in[Clk] (IN)
                         net (fo=66, unset)           0.973     0.973    wci/wci_decode/ctl_in[Clk]
                         FDRE                                         r  wci/wci_decode/my_state_r_reg[2]/C
  -------------------------------------------------------------------    -------------------
                         FDRE (Prop_fdre_C_Q)         0.518     1.491 r  wci/wci_decode/my_state_r_reg[2]/Q
                         net (fo=5, unplaced)         0.993     2.484    wci/wci_decode/wci_state[2]
                                                                      r  wci/wci_decode/ctl_out[SResp][1]_INST_0_i_2/I0
                         LUT6 (Prop_lut6_I0_O)        0.295     2.779 r  wci/wci_decode/ctl_out[SResp][1]_INST_0_i_2/O
                         net (fo=4, unplaced)         0.443     3.222    wci/wci_decode/ctl_out[SResp][1]_INST_0_i_2_n_0
                                                                      r  wci/wci_decode/FSM_onehot_my_access_r[4]_i_1/I2
                         LUT6 (Prop_lut6_I2_O)        0.124     3.346 r  wci/wci_decode/FSM_onehot_my_access_r[4]_i_1/O
                         net (fo=8, unplaced)         0.511     3.857    wci/wci_decode/my_access_r
                         FDSE                                         r  wci/wci_decode/FSM_onehot_my_access_r_reg[0]/CE
  -------------------------------------------------------------------    -------------------

                         (clock clk1 rise edge)       0.002     0.002 r
                                                      0.000     0.002 r  ctl_in[Clk] (IN)
                         net (fo=66, unset)           0.924     0.926    wci/wci_decode/ctl_in[Clk]
                         FDSE                                         r  wci/wci_decode/FSM_onehot_my_access_r_reg[0]/C
                         clock pessimism              0.000     0.926
                         clock uncertainty           -0.035     0.891
                         FDSE (Setup_fdse_C_CE)      -0.169     0.722    wci/wci_decode/FSM_onehot_my_access_r_reg[0]
  -------------------------------------------------------------------
                         required time                          0.722
                         arrival time                          -3.857
  -------------------------------------------------------------------
                         slack                                 -3.135




report_timing: Time (s): cpu = 00:00:07 ; elapsed = 00:00:08 . Memory (MB): peak = 2093.707 ; gain = 496.523 ; free physical = 13626 ; free virtual = 87791
\end{lstlisting}



\end{document}
