\documentclass{article}
\iffalse
This file is protected by Copyright. Please refer to the COPYRIGHT file
distributed with this source distribution.

This file is part of OpenCPI <http://www.opencpi.org>

OpenCPI is free software: you can redistribute it and/or modify it under the
terms of the GNU Lesser General Public License as published by the Free Software
Foundation, either version 3 of the License, or (at your option) any later
version.

OpenCPI is distributed in the hope that it will be useful, but WITHOUT ANY
WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A
PARTICULAR PURPOSE. See the GNU Lesser General Public License for more details.

You should have received a copy of the GNU Lesser General Public License along
with this program. If not, see <http://www.gnu.org/licenses/>.
\fi
\author{} % Force author to be blank
%----------------------------------------------------------------------------------------
% Paper size, orientation and margins
%----------------------------------------------------------------------------------------
\usepackage{geometry}
\geometry{
	letterpaper,			% paper type
	portrait,				% text direction
	left=.75in,				% left margin
	top=.75in,				% top margin
	right=.75in,			% right margin
	bottom=.75in			% bottom margin
 }
%----------------------------------------------------------------------------------------
% Header/Footer
%----------------------------------------------------------------------------------------
\usepackage{fancyhdr} \pagestyle{fancy} % required for fancy headers
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}
\rhead{\small{ANGRYVIPER Team}}
%----------------------------------------------------------------------------------------
% Appendix packages
%----------------------------------------------------------------------------------------
\usepackage[toc,page]{appendix}
%----------------------------------------------------------------------------------------
% Defined Commands & Renamed Commands
%----------------------------------------------------------------------------------------
\renewcommand{\contentsname}{Table of Contents}
\renewcommand{\listfigurename}{List of Figures}
\renewcommand{\listtablename}{List of Tables}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1}} % To do notes
\newcommand{\code}[1]{\texttt{#1}} % For inline code snippet or command line
%----------------------------------------------------------------------------------------
% Various pacakges
%----------------------------------------------------------------------------------------
\usepackage{hyperref} % for linking urls and lists
\usepackage{graphicx} % for including pictures by file
\usepackage{listings} % for coding language styles
\usepackage{rotating} % for sideways table
\usepackage{pifont}   % for sideways table
\usepackage{pdflscape} % for landscape view
\usepackage{longtable}
%----------------------------------------------------------------------------------------
% Table packages
%----------------------------------------------------------------------------------------
\usepackage{tabularx} % c=center,l=left,r=right,X=fill
\usepackage{float}
\floatstyle{plaintop}
\usepackage[tableposition=top]{caption}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
%----------------------------------------------------------------------------------------
% Block Diagram / FSM Drawings
%----------------------------------------------------------------------------------------
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,fit,positioning}
\usetikzlibrary{automata} % used for the fsm
%----------------------------------------------------------------------------------------
% Colors Used
%----------------------------------------------------------------------------------------
\usepackage{colortbl}
\definecolor{blue}{rgb}{.7,.8,.9}
\definecolor{ceruleanblue}{rgb}{0.16, 0.32, 0.75}
\definecolor{drkgreen}{rgb}{0,0.6,0}
\definecolor{deepmagenta}{rgb}{0.8, 0.0, 0.8}
\definecolor{cyan}{rgb}{0.0,0.6,0.6}
\definecolor{maroon}{rgb}{0.5,0,0}
%----------------------------------------------------------------------------------------
% Update the docTitle and docVersion per document
%----------------------------------------------------------------------------------------
\def\docTitle{Component Data Sheet}
\def\docVersion{1.5}
%----------------------------------------------------------------------------------------
\date{Version \docVersion} % Force date to be blank and override date with version
\title{\docTitle}
\lhead{\small{\docTitle}}

\def\comp{temp}
% do not delete this line, it is used by the auto gen script to insert latex code
\def\comp{si5351}
%GEN_COMPLC_NAME
\def\Comp{TEMP}
% do not delete this line, it is used by the auto gen script to insert latex code
\def\Comp{Si5351 }
%GEN_COMPUC_NAME
\graphicspath{ {figures/} }

\begin{document}

\section*{Summary - \Comp}
\begin{tabular}{|c|M{13.5cm}|}
	\hline
	\rowcolor{blue}
	                  &                                                                                \\
	\hline
	Name              & \comp                                                                          \\
	\hline
	Worker Type       & Device                                                                         \\
	\hline
	Version           &  v\docVersion \\
	\hline
	Release Date      &  April 2019 \\
	\hline
	Component Library &  ocpi.assets.devices \\
	\hline
	Workers           &  \comp.hdl \\
	\hline
	Tested Platforms  &  ZedBoard(PL)/Zipper, ALST4/Zipper, ML605/Zipper\\
	\hline
\end{tabular}

\section*{Functionality}
\begin{flushleft}
The \Comp{} device worker exposes the register set of the Si5351C I\textsuperscript{2}C clock generator IC\cite{siliconlabsdatasheet} and directly interfaces with the IC's INTR and EOB pins. Each register is exposed as a uchar (8-bits wide) property. The worker drives the EOB pin to ground and the INTR pin's signal is currently unused. The Si5351C SDA/SCL pins are not controlled directly by this worker, but instead by a subdevice of this worker which arbitrates I2C bus access. \\
\end{flushleft}

\section*{Block Diagrams}
\subsection*{Top level}
\begin{center}
\small
\begin{verbatim}
<!--        __________________________________________________________       -->
<!--       | FPGA                                                     |      -->
<!--       | (represented by       /\                                 |      -->
<!--       | OpenCPI platform)     | control plane interface exposes  |      -->
<!--       |                       | each Si5351C register as a       |      -->
<!--       |                _______V_____     uchar property          |      -->
<!--       | ______________|_______|_____|__                          |      -->
<!--       || si5351.hdl           |        |          (other device  |      -->
<!--       ||______________________|________|           workers on    |      -->
<!--       | /\intr |oeb   |_______|_____|              I2C bus.....) |      -->
<!--       | |      |              /\                        /\    /\ |      -->
<!--       | |      |  raw property| ........................:     :  |      -->
<!--       | |      |     interface| : ............................:  |      -->
<!--       | |      |          ____V_:_:_                             |      -->
<!--       | |      |  _______|____|_:_:_|___                         |      -->
<!--       | |      | | <>_i2c.hdl | : :     | worker/platform/card-  |      -->
<!--       | |      | |  __________|_:_:___  | specific subdevice     |      -->
<!--       | |      | | | raw prop arbiter | | worker which arbitrates|      -->
<!--       | |      | | |__________________| | I2C bus access         |      -->
<!--       | |      | |_______|_____|________|                        |      -->
<!--       | |      |         /\    /\                                |      -->
<!--       | |      |         |     | I2C bus signals                 |      -->
<!--       |_|______V_________V_____V_________________________________|      -->
<!--         |      |         |.....|... (other                              -->
<!--         |      |         |     |...  IC devices)                        -->
<!--        _|______|_________|_____|_________________________________       -->
<!--       |INTR    OEB       SDA  SCL                                |      -->
<!--       | Si5351C IC                                               |      -->
<!--       |__________________________________________________________|      -->
\end{verbatim}
\normalsize
\end{center}\pagebreak

\section*{Worker Implementation Details}
\subsection*{\comp.hdl - Property Set}
Information about the static Si5351C hardware configuration is conveyed via the \verb+clkin_present+, \verb+clkin_freq+, \verb+xtal_present+, \verb+xtal_freq+, \verb+vc_present+, \verb+outputs_present+, \verb+oeb_mode+, and \verb+intr_connected+ properties. Because these properties are designed to convey static information that is determined at build-time, their parameter attribute is set to true. Each of these properties also has its readable attribute set to true. Normally it is not recommended to set both the parameter and the readable attributes to true because readable implies unnecessary control plane infrastructure for property read accesses. Setting the parameter attribute alone to true exposes an optimized property read access mechanism for applications. This mechanism is not currently implemented, however, for device proxy slave interfaces. Because the aforementioned parameter properties are intended to be accessed via a device proxy slave interface, their readable attributes are set to true. \\

\noindent Each non-parameter property's value represents that of a Si5351C register. Each non-parameter property is a raw property. \\

\subsection*{\comp.hdl - Control Plane Timeout Value Selection}
\noindent Because I\textsuperscript{2}C transactions require additional clock cycles to complete property accesses, the control plane timeout default value (of 16) is overriden to be 131072. The intended I\textsuperscript{2}C SCL clock frequency is 250 kHz, and the I\textsuperscript{2}C read operation duration is approximated to be 32 SCL clock cycles. This results in a read access being approximately 32/(250,000 Hz) = 0.000128 sec. This corresponds to (control plane clock cycles/sec)*(0.000128 sec) clock cycles per read access. By setting the timeout to 131072, control plane clocks of up to approximately 131072/0.00128 Hz = 1.024 GHz would be supported, which is far higher than any currently possible control plane clock frequency.

\section*{Source Dependencies}
\subsection*{\comp.hdl}
\begin{itemize}
	\item assets/hdl/devices/\comp.hdl/\comp.vhd
\end{itemize}

\begin{landscape}
	\section*{Component Spec Properties}
	\begin{scriptsize}
% do not delete this line, it is used by the auto gen script to insert latex code
\begin{tabular}{|p{2cm}|p{1.5cm}|c|c|c|p{1.5cm}|p{1cm}|p{7cm}|}
\hline
\rowcolor{blue}
Name                 & Type   & SequenceLength & ArrayDimensions & Accessibility       & Valid Range & Default & Usage
\\
\hline
- & - & - & - & - & -  & - & -
\\
\hline
\end{tabular}
%GEN_SPEC_TABLE
	\end{scriptsize}

	\section*{Worker Properties}
	\subsection*{\comp.hdl}
	\begin{scriptsize}
% do not delete this line, it is used by the auto gen script to insert latex code
%GEN_WORKER_TABLE
		\begin{longtable}[l]{|p{2cm}|p{2cm}|p{1cm}|p{2cm}|p{1.7cm}|p{1cm}|p{2.5cm}|p{1cm}|p{5.88cm}|}
			\hline
			\rowcolor{blue}
			Scope        & Name                 & Type  &ArrayDimensions& Accessibility & Padding & Valid Range  & Default & Usage \\
			\hline
			Property     & clkin\_present       & Bool  &                 & Parameter, Readable &   &              & 0       & Does this chip have an external clock as input? \\
			\hline
			Property     & clkin\_freq          & Float &                 & Parameter, Readable &   &              & 0       &       \\
			\hline
			Property     & xtal\_present        & Bool  &                 & Parameter, Readable &   &              & 0       & Does this chip have a crystal oscillator as input? \\
			\hline
			Property     & xtal\_freq           & Float &                 & Parameter, Readable &   &              & 0       &       \\
			\hline
			Property     & vc\_present          & Bool  &                 & Parameter, Readable &   &              & 0       & Does this chip have a VCXO as input? \\
			\hline
			Property     & outputs\_present     & Bool  & 8               & Parameter, Readable &   &              & 0       &       \\
			\hline
			Property     & oeb\_mode            & Enum  &                 & Parameter, Readable &   & low,high,connected&low &       \\
			\hline
			Property     & intr\_connected      & Bool  &                 & Parameter, Readable &   &              & 0       &       \\
			\hline
      Property     & dev\_status          & UChar &                 & Readable            &   &              &         & Hardware registers: 0: Device Status \\
			\hline
      Property     & int\_sts\_stcky      & UChar &                 & Volatile, Writable  &   &              &         & Hardware registers: 1: Interrupt Status Sticky \\
			\hline
      Property     & int\_sts\_mask       & UChar &                 & Readable, Writable  &	  &              &         & Hardware registers: 2: Interrupt Status Mask \\
			\hline
      Property     & out\_en\_ctl         & UChar &                 & Readable, Writable  &  	&              &         & Hardware registers: 3: Output enable control \\
			\hline
      Property     & reserved00           & UChar & 5               &                     & true&            &         & Hardware registers: 4-8: Reserved \\
			\hline
      Property     & oeb\_pin\_en         & UChar &                 & Volatile, Writable  &    	&            &         & Hardware registers: 9: OEB pin enable control mask \\
			\hline
      Property     & reserved01           & UChar & 5               &                     & true&            &         & Hardware registers: 10-14: Reserved \\
			\hline
      Property     & pll\_in\_src         & UChar &                 & Readable, Writable  &    	&            &         & Hardware registers: 15: PLL Input Source \\
			\hline
      Property     & clk\_ctl             & UChar & 8               & Readable, Writable  &     &            &         & Hardware registers: 16 - 23: Clock Control \\
			\hline
      Property     & clk30\_dis\_st       & UChar &                 & Volatile, Writable  &    	&            &         & Hardware registers: 24: Clock Disable State \\
			\hline
      Property     & clk74\_dis\_st       & UChar &                 & Volatile, Writable  &    	&            &         & Hardware registers: 25 \\
			\hline
      Property     & ms\_div\_params      & UChar & 2x8             & Readable, Writable  &     &            &         & Hardware registers: 26 - 41: Feedback Multisynth Divider Parameters (doc section 3.2) - one set per PLL (NOT per MS output) \\
			\hline
      Property     & ms\_0\_5\_params     & UChar & 6x8             & Readable, Writable  &     &            &         & Hardware registers: 42 - 89: Output Multisynth Parameters (doc section 4.1) - one set of 8 regs per MS output for the first 6 \\
			\hline
      Property     & ms\_6\_7\_params     & UChar & 2               & Readable, Writable  &     &            &         & Hardware registers: 90 - 91: Output Multisynth Parameters (doc section 4.1) - one register per MS output for the last 2 \\
			\hline
      Property     & clk67\_div           & UChar &                 & Readable, Writable  &     &            &         & Hardware registers: 92: Clock 6-7 Output divider \\
			\hline
      Property     & pad0                 & UChar & 56              &                     & true&            &         & Hardware registers: 93 - 148: Padding \\
			\hline
      Property     & ss\_params           & UChar & 13              & Readable, Writable  &     &            &         & Hardware registers: 149 - 161: Spread Spectrum Parameters \\
			\hline
      Property     & vcx                  & UChar & 3               & Readable, Writable  &     &            &         & Hardware registers: 162 - 164: VCXO Parameters \\
			\hline
      Property     & clk\_phs\_offs       & UChar & 6               & Readable, Writable  &     &            &         & Hardware registers: 165 - 170: Initial Phase Offsets \\
			\hline
      Property     & reserved02           & UChar & 6               &                     & true&            &         & Hardware registers: 171 - 176: Reserved \\
			\hline
      Property     & pll\_reset           & UChar &                 & Readable, Writable  &     &            &         & Hardware registers: 177: PLL Reset \\
			\hline
      Property     & reserved16           & UChar & 5               &                     & true&            &         & Hardware registers: 178-182: Reserved \\
			\hline
      Property     & xtal\_cl             & UChar &                 & Readable, Writable  &     &            &         & Hardware registers: 183: Crystal Internal Load Capacitance \\
			\hline
      Property     & reserved03           & UChar & 3               &                     & true&            &         & Hardware registers: 184-186: Reserved \\
			\hline
      Property     & fanout\_en           & UChar &                 & Readable, Writable  &     &            &         & Hardware registers: 187: Fanout enable \\
			\hline
      Property     & reserved04           & UChar & 68              &                     & true&            &         & Hardware registers: 188-255: Reserved \\
			\hline
		\end{longtable}


	\end{scriptsize}

	\section*{Component Ports}
	\begin{scriptsize}
% do not delete this line, it is used by the auto gen script to insert latex code
%GEN_PORT_TABLE
	\end{scriptsize}

	\section*{Worker Interfaces}
	\subsection*{\comp.hdl}
	\begin{scriptsize}
%GEN_INTERFACE_TABLE
		\begin{tabular}{|M{2cm}|M{1.5cm}|c|c|M{13.85cm}|}
			\hline
			\rowcolor{blue}
			Type & Name & DataWidth & Advanced & Usage \\
			\hline
			RawProp
			& rprops
			& -
			& Master=true
			& \begin{flushleft}Raw properties connection for slave I2C device worker\end{flushleft}\\
			\hline
			ControlInterface
			& -
			& -
			& Timeout=131072
			& \begin{flushleft}Control clock cycles required to complete property  read/write. I2C transactions require additional clock cycles to complete than the default of 16. \end{flushleft}\\
			\hline
		\end{tabular}
	\end{scriptsize}
\end{landscape}

\section*{Control Timing and Signals}
\subsection*{\comp.hdl}
\begin{flushleft}
The \Comp{} HDL device worker uses the clock from the Control Plane and standard Control Plane signals. There are no ports and therefore no latency or pipeline delay concerns to consider.
\end{flushleft}

\section*{Performance and Resource Utilization}
\subsubsection*{\comp.hdl}

\begin{thebibliography}{1}

\bibitem{siliconlabsdatasheet} SI5351 A/B/C-B I2C-PROGRAMMABLE ANY-FREQUENCY CMOS CLOCK GENERATOR + VCXO \\
\url{https://www.silabs.com/documents/public/data-sheets/Si5351-B.pdf}

%this bibitem belongs in proxy datasheet, not here
%\bibitem{an619} Manually Generating an Si5351 Register Map\\
%\url{https://www.silabs.com/Support Documents/TechnicalDocs/AN619.pdf}

\end{thebibliography}

\end{document}
