\iffalse
This file is protected by Copyright. Please refer to the COPYRIGHT file
distributed with this source distribution.

This file is part of OpenCPI <http://www.opencpi.org>

OpenCPI is free software: you can redistribute it and/or modify it under the
terms of the GNU Lesser General Public License as published by the Free Software
Foundation, either version 3 of the License, or (at your option) any later
version.

OpenCPI is distributed in the hope that it will be useful, but WITHOUT ANY
WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A
PARTICULAR PURPOSE. See the GNU Lesser General Public License for more details.

You should have received a copy of the GNU Lesser General Public License along
with this program. If not, see <http://www.gnu.org/licenses/>.
\fi

%----------------------------------------------------------------------------------------
% Update the docTitle and docVersion per document
%----------------------------------------------------------------------------------------
\def\docTitle{Component Data Sheet}
\def\docVersion{1.5}
%----------------------------------------------------------------------------------------
\input{../../../../../../doc/av/tex/snippets/LaTeX_Header.tex}
\date{Version \docVersion} % Force date to be blank and override date with version
\title{\docTitle}
\lhead{\small{\docTitle}}

\usepackage{longtable} % for long possibly multi-page tables

\def\comp{iqstream\_to\_timeiq}
\def\ecomp{iqstream_to_timeiq}
\def\Comp{IQstream to TimeIQ}
\graphicspath{ {figures/} }

\begin{document}

\section*{Summary - \Comp}
\begin{tabular}{|c|M{13.5cm}|}
	\hline
	\rowcolor{blue}
	                  &                        							\\
	\hline
	Name              & \comp                  							\\
	\hline
	Worker Type       & Application            							\\
	\hline
	Version           & \docVersion                  							\\
	\hline
	Release Date      & 4/2019           						\\
	\hline
	Component Library & ocpi.assets.misc\_comps 					\\
	\hline
	Workers           & \comp.hdl              							\\
	\hline
	Tested Platforms  & isim, xsim, modelsim, zed, matchstiq\_z1, e3xx, alst4, ml605	\\
	\hline
\end{tabular}
	
\section*{Functionality}
\begin{flushleft}
	The \Comp{} component adapts the iqstream protocol to the TimeStamped\_IQ protocol.
\end{flushleft}

\section*{Worker Implementation Details}
\subsection*{\comp.hdl}
\begin{flushleft}
	The TimeStamped\_IQ protocol consists of multiple opcodes which include complex IQ samples, and the iqstream protocol consists only of complex IQ samples. The \comp{} worker forwards data from the input port to the output port and applies the samples opcode to it.
\end{flushleft}

\section*{Block Diagrams}
\subsection*{Top level}
\begin{center}
	\begin{tikzpicture}[% List of styles applied to all, to override specify on a case-by-case
			every node/.style={	
				align=center,  		% use this so that the "\\" for line break works
				minimum size=2cm	% creates space above and below text in rectangle
			},
			every edge/.style={draw,thick}
		]
		\node[rectangle,ultra thick,draw=black,fill=blue](R2){\Comp};
		\node[rectangle,draw=white,fill=white](R3)[left= of R2]{``in" \\ Signed complex samples};
		\node[rectangle,draw=white,fill=white](R4)[right= of R2]{``out" \\ Signed complex samples\\ with other opcodes};
		\path[->]
		(R3)edge []	node [] {} (R2)
		(R2)edge []	node [] {} (R4)
		;
	\end{tikzpicture}
\end{center}

\section*{Source Dependencies}
\subsection*{\comp.hdl}
\begin{itemize}
	\item bsp\_picoflexor/components/\comp.hdl/\comp.vhd
\end{itemize}

\begin{landscape}
	\section*{Component Spec Properties}
	There are no component spec properties for this component
	
	\section*{Worker Properties}
	There are no worker implementation-specific properties for this component
	
	\section*{Component Ports}
	\begin{scriptsize}
		\begin{tabular}{|M{2cm}|M{1.5cm}|M{4cm}|c|c|M{9cm}|}
			\hline
			\rowcolor{blue}
			Name & Producer & Protocol                       & Optional & Advanced & Usage                                  		\\
			\hline
			in   & false    & iqstream\_protocol			 & false    & -        & Signed complex samples 						\\
			\hline
			out  & true     & TimeStamped\_IQ-prot           & false    & -        & Signed complex samples plus other operations   \\
			\hline
		\end{tabular}
	\end{scriptsize}
	\section*{Worker Interfaces}
	\subsection*{\comp.hdl}
	\begin{scriptsize}
		\begin{tabular}{|M{2cm}|M{1.5cm}|c|c|M{12cm}|}
			\hline
			\rowcolor{blue}
			Type            & Name & DataWidth & Advanced   & Usage                                    		\\
			\hline
			StreamInterface & in   & 32        & - 			& Signed complex samples 						\\
			\hline
			StreamInterface & out  & 32        & - 			& Signed complex samples plus other operations	\\
			\hline
		\end{tabular}
	\end{scriptsize}
\end{landscape}

\section*{Control Timing and Signals}
\begin{flushleft}
	The \comp worker{} uses the clock from the Control Plane and standard Control Plane signals.\\
\end{flushleft}

\begin{landscape}
\section*{Worker Configuration Parameters}
\subsubsection*{\comp.hdl}
\input{../../\ecomp.hdl/configurations.inc}
\section*{Performance and Resource Utilization}
\input{../../\ecomp.hdl/utilization.inc}
\end{landscape}

\section*{Test and Verification}
\begin{flushleft}
	The input file contains 5824 bytes of arbitrary data. It is the same input file used for the TimeIQ\_to\_IQstream unit test. The expected output waveform is identical to the input file.
\end{flushleft}
\end{document}
