\documentclass{article}
\iffalse
This file is protected by Copyright. Please refer to the COPYRIGHT file
distributed with this source distribution.

This file is part of OpenCPI <http://www.opencpi.org>

OpenCPI is free software: you can redistribute it and/or modify it under the
terms of the GNU Lesser General Public License as published by the Free Software
Foundation, either version 3 of the License, or (at your option) any later
version.

OpenCPI is distributed in the hope that it will be useful, but WITHOUT ANY
WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A
PARTICULAR PURPOSE. See the GNU Lesser General Public License for more details.

You should have received a copy of the GNU Lesser General Public License along
with this program. If not, see <http://www.gnu.org/licenses/>.
\fi

\author{} % Force author to be blank
%----------------------------------------------------------------------------------------
% Paper size, orientation and margins
%----------------------------------------------------------------------------------------
\usepackage{geometry}
\geometry{
	letterpaper,			% paper type
	portrait,				% text direction
	left=.75in,				% left margin
	top=.75in,				% top margin
	right=.75in,			% right margin
	bottom=.75in			% bottom margin
 }
%----------------------------------------------------------------------------------------
% Header/Footer
%----------------------------------------------------------------------------------------
\usepackage{fancyhdr} \pagestyle{fancy} % required for fancy headers
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}
\rhead{\small{ANGRYVIPER Team}}
%----------------------------------------------------------------------------------------
% Appendix packages
%----------------------------------------------------------------------------------------
\usepackage[toc,page]{appendix}
%----------------------------------------------------------------------------------------
% Defined Commands & Renamed Commands
%----------------------------------------------------------------------------------------
\renewcommand{\contentsname}{Table of Contents}
\renewcommand{\listfigurename}{List of Figures}
\renewcommand{\listtablename}{List of Tables}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1}} % To do notes
\newcommand{\code}[1]{\texttt{#1}} % For inline code snippet or command line
%----------------------------------------------------------------------------------------
% Various pacakges
%----------------------------------------------------------------------------------------
\usepackage{hyperref} % for linking urls and lists
\usepackage{graphicx} % for including pictures by file
\usepackage{listings} % for coding language styles
\usepackage{rotating} % for sideways table
\usepackage{pifont}   % for sideways table
\usepackage{pdflscape} % for landscape view
\usepackage{longtable}
%----------------------------------------------------------------------------------------
% Table packages
%----------------------------------------------------------------------------------------
\usepackage{tabularx} % c=center,l=left,r=right,X=fill
\usepackage{float}
\floatstyle{plaintop}
\usepackage[tableposition=top]{caption}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
%----------------------------------------------------------------------------------------
% Block Diagram / FSM Drawings
%----------------------------------------------------------------------------------------
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,fit,positioning}
\usetikzlibrary{automata} % used for the fsm
%----------------------------------------------------------------------------------------
% Colors Used
%----------------------------------------------------------------------------------------
\usepackage{colortbl}
\definecolor{blue}{rgb}{.7,.8,.9}
\definecolor{ceruleanblue}{rgb}{0.16, 0.32, 0.75}
\definecolor{drkgreen}{rgb}{0,0.6,0}
\definecolor{deepmagenta}{rgb}{0.8, 0.0, 0.8}
\definecolor{cyan}{rgb}{0.0,0.6,0.6}
\definecolor{maroon}{rgb}{0.5,0,0}
%----------------------------------------------------------------------------------------
% Update the docTitle and docVersion per document
%----------------------------------------------------------------------------------------
\def\docTitle{Worker Data Sheet}
\def\docVersion{1.5}
%----------------------------------------------------------------------------------------
\date{Version \docVersion} % Force date to be blank and override date with version
\title{\docTitle}
\lhead{\small{\docTitle}}

\def\comp{tx}
\def\Comp{Fmcomms 2/3 TX}
\graphicspath{ {figures/} }

\begin{document}

\section*{Summary - FMCOMMS2/3 TX Worker}
\begin{longtable}{|p{\dimexpr0.5\textwidth-2\tabcolsep\relax}
                  |p{\dimexpr0.5\textwidth-2\tabcolsep\relax}|}
	\hline
	\rowcolor{blue}
	                  &                                        \\
	\hline
	Package Prefix    & ocpi.core \\
	\hline
	Component         & tx \\
	\hline
	Name              & fmcomms\_2\_3\_tx                      \\
	\hline
	Authoring Model   & rcc                                    \\
	\hline
	Version          & 1 \\
	\hline
	OpenCPI Release & v\docVersion ~ (released 4/2019) \\
	\hline
	Tested Platforms  & Zedboard (xilinx13\_3), ML605 (x86\_64 CentOS 7) \\
	\hline
	Slaves       & - \\
	\hline
	ACI ``Slaves" &
    \begin{itemize}
      \item ad9361\_config\_proxy.rcc
      \item ad9361\_data\_sub.hdl
    \end{itemize} \\
	\hline
\end{longtable}

\section*{Functionality}

	This worker is an endpoint proxy used to control a single TX channel of an instance of the FMCOMMS2 or the FMCOMMS3 RF transceiver card. Multiple TX channels on the same FMCOMMS2/3 card are not yet supported. This worker has two parameterized build configurations: one for FMCOMMS2 (\verb+TYPE_p+ parameter property value of 'fmcomms2') and one for FMCOMMS3 (\verb+TYPE_p+ parameter property value of 'fmcomms3'). Each property has a max, min, and step value associated with it.  These associated properties are available to be used by application developers for reading back information about the functionality of the interface during runtime if necessary.\par\medskip
\noindent This worker implements a common interface that is intended to be used across multiple platforms. All platforms will have the same property interface to allow applications to be ported seamlessly to other platforms. It is also intended to be a simple interface that encompasses functionality that all TX interfaces will have but not any specialty functionality that only some TX interfaces will have.\par\medskip

\section*{Worker Implementation Details}
This worker controls the filtering, gain, tuning frequency, and the sample rate of the AD9361 on the FMCOMMS2/3 RF transciever card.  Each of these are described below in their own section.

\subsection*{Clock Generation}
The AD9361 contains multiple PLLs which all use the same external-to-the-AD9361 clock source. This external source can be either:
\begin{itemize}
\item a crystal connected to the AD9361 XTALP/N pins (a 40 MHz [nominal] crystal is connected on FMCOMMS2/3), or
\item an external clock source connected to the AD9361 XTALN pin (the REF\_CLK SMA connector is connected on FMCOMMS2/3).
\end{itemize}
This worker's \verb+config+ property's \verb+reference_clk_rate_Hz+ struct member should contain the value of the clock frequency in Hz (whether crystal or external). If the default FMCOMMS2/3 hardware is to be used (i.e. crystal used), the \verb+config+ property's \verb+are_using_REF_CLK_SMA+ value should be left to its default value (of false). If the FMCOMMS2/3 has an external clock connected, the \verb+config+ property's \verb+are_using_REF_CLK_SMA+ value must be set to true. Only the default settings (i.e. crystal used) have been verified.
\subsection*{Filtering}
In the RF section of the AD9361 transceiver, there are no filtering elements.\par\medskip
\noindent The AD9361's baseband Tx
signal path is composed of two programmable analog low-pass
filters, a 12-bit DAC, and four stages of digital interpolation
filters \cite{adi_ug570}.
\noindent The baseband filters are as follows:
\begin{itemize}
\item PROG TX FIR (\textit{\textbf{disabled by this worker}})
\begin{itemize}
\item digital filter whose interpolation factor is configurable to 1, 2, or 4, and whose taps are customizable with 16-bit values up to 128 taps
\end{itemize}
\item Tx HB1 filter (Half-Band)
\begin{itemize}
\item digital half-band interpolation filter with fixed-coefficient tap set with interpolation factor of 2 (or can bypass filter, effectively interpolating by 1)
\end{itemize}
\item Tx HB2 filter (Half-Band)
\begin{itemize}
\item digital half-band interpolation filter with fixed-coefficient tap set with interpolation factor of 2 (or can bypass filter, effectively interpolating by 1)
\end{itemize}
\item Tx HB3/INT3 filter (Half-Band / Interpolation)
\begin{itemize}
\item digital half-band interpolation filter with selectable fixed-coefficient tap sets with interpolation factors of 1 (bypasses filter), 2, or 3
\end{itemize}
\item Tx BB LPF (BaseBand Low-Pass Filter)
\begin{itemize}
\item analog third-order Butterworth low-pass filter with a programmable 3dB corner frequency
\end{itemize}
\item Tx Secondary LPF (Low-Pass Filter)
\begin{itemize}
\item analog single-pole low-pass filter with a programmable 3dB corner frequency
\end{itemize}
\end{itemize}
Changes to the AD9361 TX sample rate (via the \verb+sample_rate_MHz+ property) or the RX sample rate can affect the TX HB digital filter settings. Note that the setting of both the analog and the digital filters will determine the overall effective baseband bandwidth. Values written to the \verb+bb_cutoff_frequency_MHz+ property are rounded to the nearest Hz and passed to the No-OS ad9361\_set\_tx\_rf\_bandwidth() API call, which attempts to set the overall baseband -3dB bandwidth to \textit{approximately} the requested (rounded to nearest Hz) value. Read requests to the \verb+bb_cutoff_frequency_MHz+ property will simply return the value of the No-OS ad9361\_get\_tx\_rf\_bandwidth() API call, \textit{which is known to not have floating-point precision as well as to represent a crude approximation of the current nominal value}. Work is expected to be done in the future to modify read requests to return the double floating point-precision nominal value instead of using the No-OS API.
\subsection*{Gain}
The AD9361 supports a manual (non-automatic) TX attenuation setting. The vendor does not document whether the TX attenuation setting is pre-mixer (baseband), post-mixer (RF), or both, so it was arbitrarily chosen to map the \verb+rf_gain_dB+ property (as opposed to the \verb+bb_gain_dB+ property) to the AD9361 TX attenuation setting. This worker's \verb+rf_gain_dB+ property sets the AD9361 TX attenuation (as the negative of the gain) and reads back the nominal value with exact precision.
\subsection*{Tuning}
The AD9361 has a mixer for upconverting from baseband to RF. The mixer LO is source by a PLL which is sourced by the external-to-the-AD9361 reference clock, which is a 40 MHz crystal on the FMCOMMS2/3 PCB. This worker's \verb+frequency_MHz+ property sets the AD9361 TX center frequency and reads back the nominal value with double floating point precision.

\subsection*{Sample Rate}
The AD9361 TX sampling clock is generated by an on-AD9361 PLL which is sourced by the external-to-the-AD9361 reference clock, which is a 40 MHz crystal on the FMCOMMS2/3 PCB. This worker's \verb+sample_rate_MHz+ property sets the AD9361 TX sample rate and reads back the nominal value with double floating point precision. Note that the \verb+sample_rate_MHz+ property as it currently exists corresponds to the post-TX FIR complex sample rate, and the FIR is always disabled by this worker.

\newpage

\section*{Source Dependencies}
\begin{itemize}
	\item assets/hdl/cards/fmcomms\_2\_3\_tx.rcc/fmcomms\_2\_3\_tx.cc
	\item assets/hdl/cards/fmcomms\_2\_3\_rx.rcc/include/ad9361/ad9361\_common.h
	\item assets/hdl/cards/fmcomms\_2\_3\_rx.rcc/include/ad9361/readers\_ad9361\_bb\_pll.h
	\item assets/hdl/cards/fmcomms\_2\_3\_rx.rcc/include/ad9361/readers\_ad9361\_bb\_rx\_adc.h
	\item assets/hdl/cards/fmcomms\_2\_3\_rx.rcc/include/ad9361/readers\_ad9361\_bb\_rx\_filters\_digital.h
	\item assets/hdl/cards/fmcomms\_2\_3\_tx.rcc/include/ad9361/readers\_ad9361\_bb\_tx\_dac.h
	\item assets/hdl/cards/fmcomms\_2\_3\_tx.rcc/include/ad9361/readers\_ad9361\_bb\_tx\_filters\_analog.h
	\item assets/hdl/cards/fmcomms\_2\_3\_tx.rcc/include/ad9361/readers\_ad9361\_bb\_tx\_filters\_digital.h
	\item assets/hdl/cards/fmcomms\_2\_3\_tx.rcc/include/ad9361/readers\_ad9361\_bb\_tx\_gain.h
	\item assets/hdl/cards/fmcomms\_2\_3\_rx.rcc/include/ad9361/readers\_ad9361\_cfg.h
	\item assets/hdl/cards/fmcomms\_2\_3\_tx.rcc/include/ad9361/readers\_ad9361\_rf\_tx\_pll.h
	\item assets/hdl/cards/fmcomms\_2\_3\_tx.rcc/include/ad9361/writers\_ad9361\_bb\_tx\_dac.h
	\item assets/hdl/cards/fmcomms\_2\_3\_tx.rcc/include/ad9361/writers\_ad9361\_bb\_tx\_filters\_analog.h
	\item assets/hdl/cards/fmcomms\_2\_3\_tx.rcc/include/ad9361/writers\_ad9361\_rf\_tx\_pll.h
	\item assets/hdl/cards/fmcomms\_2\_3\_tx.rcc/include/ad9361/writers\_ad9361\_tx\_gain.h
	\item assets/hdl/cards/fmcomms\_2\_3\_tx.rcc/include/ocpi\_component\_prop\_type\_helpers.h
	\item assets/hdl/cards/fmcomms\_2\_3\_tx.rcc/include/worker\_prop\_parsers\_ad9361\_config\_proxy.h
\end{itemize}

\begin{landscape}
	\section*{Component Spec Properties}
	\begin{scriptsize}
		\begin{tabular}{|p{4cm}|c|c|c|c|c|c|p{8cm}|}
			\hline
			\rowcolor{blue}
			Name                                & Type   & Sequence & Array      & Accessibility       & Valid Range & Default & Usage                                                                                      \\
			\rowcolor{blue}
			                                    &        & Length   & Dimensions &                     &             &         &                                                                                            \\
			\hline
			\verb+rf_gain_dB+                   & double & -        & -          & Readable, Writable  & -           & 0       & The value of the RF gain stage of the receiver                                            \\
			\hline
			\verb+rf_gain_max_dB+               & double & -        & -          & Volatile, Writable & -           & 0       & Maximum valid value for RF gain                                                            \\
			\hline
			\verb+rf_gain_min_dB+               & double & -        & -          & Volatile, Writable & -           & 0       & Minimum valid value for RF gain                                                            \\
			\hline
			\verb+rf_gain_step_dB+              & double & -        & -          & Volatile, Writable & -           & 0       & Minimum granularity for changes in RF gain                                                 \\
			\hline
			\verb+bb_gain_dB+                   & double & -        & -          & Readable, Writable  & -           & 0       & The value of the baseband gain stage of the receiver                                       \\
			\hline
			\verb+bb_gain_max_dB+               & double & -        & -          & Volatile, Writable & -           & 0       & Maximum valid value for baseband gain                                                      \\
			\hline
			\verb+bb_gain_min_dB+               & double & -        & -          & Volatile, Writable & -           & 0       & Minimum valid value for baseband gain                                                      \\
			\hline
			\verb+bb_gain_step_dB+              & double & -        & -          & Volatile, Writable & -           & 0       & Minimum granularity for changes in baseband gain                                           \\
			\hline
			\verb+frequency_MHz+                & double & -        & -          & Readable, Writable  & -           & 0       & The value for the tuned center frequency of the incoming RF samples                        \\
			\hline
			\verb+frequency_max_MHz+            & double & -        & -          & Volatile, Writable & -           & 0       & Maximum valid value for frequency                                                          \\
			\hline
			\verb+frequency_min_MHz+            & double & -        & -          & Volatile, Writable & -           & 0       & Minimum valid value for frequency                                                          \\
			\hline
			\verb+frequency_step_MHz+           & double & -        & -          & Volatile, Writable & -           & 0       & Minimum granularity for changes in frequency                                               \\
			\hline
			\verb+sample_rate_MHz+              & double & -        & -          & Readable, Writable  & -           & 0       & Sample rate of the incoming RF samples                                                     \\
			\hline
			\verb+sample_rate_max_MHz+          & double & -        & -          & Volatile, Writable & -           & 0       & Maximum valid value for sample rate                                                        \\
			\hline
			\verb+sample_rate_min_MHz+          & double & -        & -          & Volatile, Writable & -           & 0       & Minimum valid value for sample rate                                                        \\
			\hline
			\verb+sample_rate_step_MHz+         & double & -        & -          & Volatile, Writable & -           & 0       & Minimum granularity for changes in sample rate                                             \\
			\hline
			\verb+rf_cutoff_frequency_MHz+      & double & -        & -          & Readable, Writable  & -           & 0       & The effective cutoff frequency, i.e. half of the bandwidth, for all filtering that is done in the RF stage of the receiver.      \\
			\hline
			\verb+rf_cutoff_frequency_max_MHz+  & double & -        & -          & Volatile, Writable & -           & 0       & Maximum valid value for RF cutoff frequency                                                \\
			\hline
			\verb+rf_cutoff_frequency_min_MHz+  & double & -        & -          & Volatile, Writable & -           & 0       & Minimum valid value for RF cutoff frequency                                                \\
			\hline
			\verb+rf_cutoff_frequency_step_MHz+ & double & -        & -          & Volatile, Writable & -           & 0       & Minimum granularity for changes in RF cutoff frequency                                     \\
			\hline
			\verb+bb_cutoff_frequency_MHz+      & double & -        & -          & Readable, Writable  & -           & 0       & The effective cutoff frequency, i.e. half of the bandwidth, for all filtering that is done in the baseband stage of the receiver.\\
			\hline
			\verb+bb_cutoff_frequency_max_MHz+  & double & -        & -          & Volatile, Writable & -           & 0       & Maximum valid value for baseband cutoff frequency                                          \\
			\hline
			\verb+bb_cutoff_frequency_min_MHz+  & double & -        & -          & Volatile, Writable & -           & 0       & Minimum valid value for baseband cutoff frequency                                          \\
			\hline
			\verb+bb_cutoff_frequency_step_MHz+ & double & -        & -          & Volatile, Writable & -           & 0       & Minimum granularity for changes in baseband cutoff frequency                               \\
			\hline
		\end{tabular}
	\end{scriptsize}
\pagebreak
	\section*{Worker Properties}
	\subsection*{\comp.rcc}
	\begin{scriptsize}
		\begin{longtable}{|p{1.8cm}|p{4.1cm}|p{1cm}|c|c|p{1.6cm}|p{3.7cm}|p{3.7cm}|p{2.5cm}|}
			\hline
			\rowcolor{blue}
			Type         & Name                                & Type & Sequence & Array      & Accessibility/ & Valid Range  & Default & Usage                                                                                                                                                                                                                       \\
			\rowcolor{blue}
			             &                                     &      & Length   & Dimensions & Advanced       &              &         &                                                                                                                                                                                                                             \\
			\hline
			Property     & \verb+fmcomms_num+                   & UShort &-        & -          & Parameter & 2, 3 & 3 & Valid values are 2 or 3.\\
			\hline
			Property     & \verb+TYPE_p+                   & Enum &-        & -          & Parameter & fmcomms2, fmcomms3 & \verb+fmcomms_num+ == 2 ? fmcomms2 : fmcomms3 & The purpose of this property is to provide the option for     an application XML to specify this property in order to enforce use of a parameterized build for a     particular frontend type.\\
			\hline
			Property     & \verb+NOT_SUPPORTED_p+                   & Double&-        & -          & Parameter & -1 & -1 & This value, when assigned to a frontend property, e.g. \verb+rf_gain_dB+, indicates that the frontend setting corresponding to said property is not supported by the frontend hardware controlled by this worker.
			 \\
			\hline
			Property     & \verb+AD9361_TX_BBBW_NO_OS_MAX_MHZ_p+ & Double & -       & -          & Parameter & Standard & 20 & AD9361\_Reference\_Manual\_UG-570.pdf ``BBBW is half the complex bandwidth
        and coerced between 20 MHz to 0.625 MHz'' - for No-OS's enforcement of
        this fact, see No-OS ad9361\_tx\_bb\_analog\_filter\_calib()  \\
			\hline
			Property     & \verb+AD9361_TX_BBBW_NO_OS_MIN_MHZ_p+ & Double & -       & -          & Parameter & Standard & 0.625 & AD9361\_Reference\_Manual\_UG-570.pdf ``BBBW is half the complex bandwidth
        and coerced between 20 MHz to 0.625 MHz'' - for No-OS's enforcement of
        this fact, see No-OS ad9361\_tx\_bb\_analog\_filter\_calib()  \\
			\hline
			Property     & \verb+AD9361_TX_ATTENUATION_MAX_MILLIDB_P+ & Double & -       & -          & Parameter & 89.75 & 89.75 & - \\
			\hline
			Property     & \verb+AD9361_TX_ATTENUATION_MIN_MILLIDB_P+ & Double & -       & -          & Parameter & 0 & 0 & - \\
			\hline
			Property     & \verb+RF_GAIN_MAX_DB_p+ & Double & -       & -          & Parameter & -\verb+AD9361_TX_ATTENUATION_MIN_MILLIDB_P+ & -\verb+AD9361_TX_ATTENUATION_MIN_MILLIDB_P+ & - \\
			\hline
			Property     & \verb+RF_GAIN_MIN_DB_p+ & Double & -       & -          & Parameter & -\verb+AD9361_TX_ATTENUATION_MAX_MILLIDB_P+ & -\verb+AD9361_TX_ATTENUATION_MAX_MILLIDB_P+ & - \\
			\hline
			Property     & \verb+RF_GAIN_STEP_DB_p+ & Double & -       & -          & Parameter & 0.25 & 0.25 & - \\
			\hline
			Property     & \verb+BB_GAIN_MAX_DB_p+ & Double & -       & -          & Parameter & \verb+NOT_SUPPORTED_p+ & \verb+NOT_SUPPORTED_p+ & - \\
			\hline
			Property     & \verb+BB_GAIN_MIN_DB_p+ & Double & -       & -          & Parameter & \verb+NOT_SUPPORTED_p+ & \verb+NOT_SUPPORTED_p+ & - \\
			\hline
			Property     & \verb+BB_GAIN_STEP_DB_p+ & Double & -       & -          & Parameter & \verb+NOT_SUPPORTED_p+ & \verb+NOT_SUPPORTED_p+ & - \\
			\hline
			Property     & \verb+FREQUENCY_MAX_MHZ_p+                   & Double&-        & -          & Parameter & -1 & \verb+fmcomms_num+ == 2 ? 2500 : 6000 & - \\
			\hline
			Property     & \verb+FREQUENCY_MIN_MHZ_p+                   & Double&-        & -          & Parameter & -1 & \verb+fmcomms_num+ == 2 ? 2400 : 70 & - \\
			\hline
			Property     & \verb+SAMPLE_RATE_MAX_MHZ_p+                   & Double&-        & -          & Parameter & -1 & 61.44 & - \\
			\hline
			Property     & \verb+SAMPLE_RATE_MIN_MHZ_p+                   & Double&-        & -          & Parameter & -1 & 2.08334 & Note that the AD9361 precision is double(25/12), and the No-OS implementation's precision is 2.083334, but we set it to 2.08334 to avoid confusion since an OpenCPI bug does not correctly implement the precision for 2.083334 (OpenCPI rounds it to 2.08334) \\
			\hline
			Property     & \verb+RF_CUTOFF_FREQUENCY_MAX_DB_p+ & Double & -       & -          & Parameter & \verb+NOT_SUPPORTED_p+ & \verb+NOT_SUPPORTED_p+ & - \\
			\hline
			Property     & \verb+RF_CUTOFF_FREQUENCY_MIN_DB_p+ & Double & -       & -          & Parameter & \verb+NOT_SUPPORTED_p+ & \verb+NOT_SUPPORTED_p+ & - \\
			\hline
			Property     & \verb+RF_CUTOFF_FREQUENCY_STEP_DB_p+ & Double & -       & -          & Parameter & \verb+NOT_SUPPORTED_p+ & \verb+NOT_SUPPORTED_p+ & - \\
			\hline
			Property     & \verb+BB_CUTOFF_FREQUENCY_MAX_DB_p+ & Double & -       & -          & Parameter & \verb+AD9361_TX_BBBW_NO_OS_MAX_MHZ+ * 1.6 & \verb+AD9361_TX_BBBW_NO_OS_MAX_MHZ+ * 1.6 &
The maximum configurable cutoff frequency in MHz of the FMCOMMS2/3's AD9361's third-order Butterworth Tx anti-imaging filter. The Tx filter is normally calibrated to 1.6x the BBBW. For more information, see AD9361\_Reference\_Manual\_UG-570    .pdf p. 9.

			\\
			\hline
			Property     & \verb+BB_CUTOFF_FREQUENCY_MIN_DB_p+ & Double & -       & -          & Parameter & \verb+AD9361_TX_BBBW_NO_OS_MIN_MHZ+ * 1.6 & \verb+AD9361_TX_BBBW_NO_OS_MIN_MHZ+ * 1.6 &
The minimum configurable cutoff frequency in MHz of the FMCOMMS2/3's AD9361's third-order Butterworth Tx anti-imaging filter. The Tx filter is normally calibrated to 1.6x the BBBW. For more information, see AD9361\_Reference\_Manual\_UG-570    .pdf p. 9.

			\\
			\hline
			SpecProperty & \verb+rf_gain_dB+                   & Double&-        & -          & Volatile, ReadSync, WriteSync & see \verb+rf_gain_min_dB+, \verb+rf_gain_max_dB+ & -1       & The value of the RF gain stage of the receiver. Note this is not \verb+NOT_SUPPORTED_p+, -1 is a perfectly valid value.
When a write to the property occurs, this property's written value is
        applied to hardware. When a read of this property occurs, the read value
        is the (nominal) in-situ value (actual value which is currently assigned in
        hardware, which may be slightly different than a previously written
        property value due to rounding  that occurs before writing hardware
        register values and/or No-OS API rounding) with double floating point
        precision.
			 \\
			\hline
			SpecProperty & \verb+bb_gain_dB+                   & Double&-        & -          & WriteSync      & see \verb+bb_gain_min_dB+, \verb+bb_gain_max_dB+ & \verb+NOT_SUPPORTED_p+ & The value of the baseband gain stage of the receiver.
When a write to the property occurs, this property's written value is
        applied to hardware. When a read of this property occurs, the read value
        is the (nominal) in-situ value (actual value which is currently assigned in
        hardware, which may be slightly different than a previously written
        property value due to rounding  that occurs before writing hardware
        register values and/or No-OS API rounding) with double floating point
        precision.
			 \\
			\hline
			SpecProperty & \verb+frequency_MHz+                & Double&-        & -          & Volatile, ReadSync, WriteSync      & see \verb+frequency_min_MHz+, \verb+frequency_max_MHz+ & 2400     & The value for the tuned center frequency of the incoming RF samples.
			When a write to the property occurs, this property's written value is
        applied to hardware. When a read of this property occurs, the read value
        is the (nominal) in-situ value (actual value which is currently assigned in
        hardware, which may be slightly different than a previously written
        property value due to rounding  that occurs before writing hardware
        register values and/or No-OS API rounding) with double floating point
        precision.
			 \\
			\hline
			SpecProperty & \verb+sample_rate_MHz+              & Double&-        & -          & Volatile, ReadSync, WriteSync      & see \verb+sample_rate_min_MHz+, \verb+sample_rate_max_MHz+ & 30.72   & Sample rate of the incoming RF samples.                                                                                                                                                                                      			When a write to the property occurs, this property's written value is
        applied to hardware. When a read of this property occurs, the read value
        is the (nominal) in-situ value (actual value which is currently assigned in
        hardware, which may be slightly different than a previously written
        property value due to rounding  that occurs before writing hardware
        register values and/or No-OS API rounding) with double floating point
        precision.
			 \\
			\hline
			SpecProperty & \verb+rf_cutoff_frequency_MHz+      & Double&-        & -          & WriteSync      & see \verb+rf_cutoff_frequency_min_MHz+, \verb+rf_cutoff_frequency_max_MHz+         & \verb+NOT_SUPPORTED_p+ &
			When a write to the property occurs, this property's written value is
        applied to hardware. When a read of this property occurs, the read value
        is the (nominal) in-situ value (actual value which is currently assigned in
        hardware, which may be slightly different than a previously written
        property value due to rounding  that occurs before writing hardware
        register values and/or No-OS API rounding) with double floating point
        precision.
			 \\
			\hline
			SpecProperty & \verb+bb_cutoff_frequency_MHz+      & Double&-        & -          & Volatile, ReadSync, WriteSync      & see \verb+bb_cutoff_frequency_min_MHz+, \verb+bb_cutoff_frequency_max_MHz+         & 18      & The effective cutoff frequency, i.e. half of the bandwidth, for all filtering that is done in the baseband stage of the receiver. The cutoff frequency in MHz of the FMCOMMS2/3's AD3961's third-order Butterworth Tx anti-imaging filter. The Tx filter is located just after the DAC in the Rx signal path and is normally calibrated to 0.8x the desired complex bandwidth of the Butterworth filter. For more information, see AD9361\_Reference\_Manual\_UG-570.pdf p. 10.                                                                                                                                  \\
			\hline
			SpecProperty & \verb+rf_gain_max_dB+               & Double& -        & -          & WriteSync & \verb+RF_GAIN_MAX_DB_p+ & \verb+RF_GAIN_MAX_DB_p+ & Maximum valid value for RF gain                                                                                                                                                                                             \\
			\hline
			SpecProperty & \verb+rf_gain_min_dB+               & Double& -        & -          & WriteSync & \verb+RF_GAIN_MIN_DB_p+ & \verb+RF_GAIN_MIN_DB_p+ & Minimum valid value for RF gain                                                                                                                                                                                             \\
			\hline
			SpecProperty & \verb+rf_gain_step_dB+              & Double& -        & -          & WriteSync      & \verb+RF_GAIN_STEP_DB_p+ & \verb+RF_GAIN_STEP_DB_p+ & Minimum granularity for changes in RF gain                                                                                                                                                                                  \\
			\hline
			SpecProperty & \verb+bb_gain_max_dB+               & Double& -        & -          & WriteSync      & \verb+BB_GAIN_MAX_MHZ_p+ & \verb+BB_GAIN_MAX_MHZ_p+ & Maximum valid value for baseband gain                                                                                                                                                                                       \\
			\hline
			SpecProperty & \verb+bb_gain_min_dB+               & Double& -        & -          & WriteSync      & \verb+BB_GAIN_MIN_MHZ_p+ & \verb+BB_GAIN_MIN_MHZ_p+ & Minimum valid value for baseband gain                                                                                                                                                                                       \\
			\hline
			SpecProperty & \verb+bb_gain_step_dB+              & Double& -        & -          & WriteSync      & \verb+BB_GAIN_STEP_DB_p+ & \verb+BB_GAIN_STEP_DB_p+ & Minimum granularity for changes in baseband gain                                                                                                                                                                            \\
			\hline
			SpecProperty & \verb+frequency_max_MHz+            & Double& -        & -          & WriteSync      & \verb+FREQUENCY_MAX_MHZ_p+ & \verb+FREQUENCY_MAX_MHZ_p+ & Maximum valid value for frequency                                                                                                                                                                                           \\
			\hline
			SpecProperty & \verb+frequency_min_MHz+            & Double& -        & -          & WriteSync      & \verb+FREQUENCY_MIN_MHZ_p+ & \verb+FREQUENCY_MIN_MHZ_p+ & Minimum valid value for frequency                                                                                                                                                                                           \\
			\hline
			SpecProperty & \verb+frequency_step_MHz+           & Double& -        & -          & ReadSync, WriteSync & LO frequency-dependent & - & Minimum granularity for changes in frequency                                                                                                                                                                                \\
			\hline
			SpecProperty & \verb+sample_rate_max_MHz+          & Double& -        & -          & WriteSync & \verb+SAMPLE_RATE_MAX_MHZ_p+ & \verb+SAMPLE_RATE_MAX_MHZ_p+ & Maximum valid value for sample rate                                                                                                                                                                                         \\
			\hline
			SpecProperty & \verb+sample_rate_min_MHz+          & Double& -        & -          & WriteSync & \verb+SAMPLE_RATE_MIN_MHZ_p+ & \verb+SAMPLE_RATE_MIN_MHZ_p+ & Minimum valid value for sample rate                                                                                                                                                                                         \\
			\hline
			SpecProperty & \verb+sample_rate_step_MHz+         & Double& -        & -          & ReadSync, WriteSync & Runtime-variable & - & Indicates the precision which will be used to evaluate the value written
        to this worker's \verb+sample_rate_MHz+ property
        before that value is applied to hardware. For example if the step is 2,
        the value written is rounded to the nearest multiple of 2 in order to
        be applied to hardware. The precision in this case is determined by the
        precision of the ad9361\_config\_proxy.rcc worker's
        \verb+rx_sampling_freq+ property.                                                                                                                                                                              \\
			\hline
			SpecProperty & \verb+rf_cutoff_frequency_max_MHz+  & Double& -        & -          & WriteSync      & \verb+RF_CUTOFF_FREQUENCY_MAX_MHZ_p+ & \verb+RF_CUTOFF_FREQUENCY_MAX_MHZ_p+ & Maximum valid value for RF cutoff frequency. \\
			\hline
			SpecProperty & \verb+rf_cutoff_frequency_min_MHz+  & Double& -        & -          & WriteSync      & \verb+RF_CUTOFF_FREQUENCY_MIN_MHZ_p+ & \verb+RF_CUTOFF_FREQUENCY_MIN_MHZ_p+  & Minimum valid value for RF cutoff frequency. \\
			\hline
			SpecProperty & \verb+rf_cutoff_frequency_step_MHz+ & Double& -        & -          & WriteSync      & \verb+RF_CUTOFF_FREQUENCY_STEP_MHZ_p+ & \verb+RF_CUTOFF_FREQUENCY_STEP_MHZ_p+ & Minimum granularity for changes in RF cutoff frequency. \\
			\hline
			SpecProperty & \verb+bb_cutoff_frequency_max_MHz+  & Double& -        & & WriteSync      & \verb+BB_CUTOFF_FREQUENCY_MAX_MHZ_p+ & \verb+BB_CUTOFF_FREQUENCY_MAX_MHZ_p+ & Maximum valid value for baseband cutoff frequency                                                                                                                                                                           \\
			\hline
			SpecProperty & \verb+bb_cutoff_frequency_min_MHz+  & Double& -        & -          & WriteSync      & \verb+BB_CUTOFF_FREQUENCY_MIN_MHZ_p+ & \verb+BB_CUTOFF_FREQUENCY_MIN_MHZ_p+ & Minimum valid value for baseband cutoff frequency                                                                                                                                                                           \\
			\hline
			SpecProperty & \verb+bb_cutoff_frequency_step_MHz+ & Double& -        & -          & ReadSync, WriteSync & Runtime-variable & - & Maximum granularity for changes in baseband cutoff frequency                                                                                                                                                                \\
			\hline
			Property & \verb+app_inst_name_ad9361_config_proxy+ &String& -        & 128        & Initial, Readable, WriteSync & Standard & ad9361\_config\_proxy & Value must match the name of the ad9361\_config\_proxy application instance. \\
			\hline
			Property & \verb+app_inst_name_ad9361_data_sub+ &String& -        & 128        & Initial, Readable, WriteSync & Standard & ad9361\_data\_sub & Value must match the name of the ad9361\_data\_sub application instance. \\
			\hline
			Property & \verb+config+ & Struct (see \hyperlink{tab1}{Table 1}) & -        & -        & Initial, Volatile, ReadSync, WriteSync & Standard & reference\_clk\_rate\_Hz 40e6,duplex\_mode FDD,are\_using\_REF\_CLK\_SMA false,SMA\_channel TX1A & Value must match the name of the ad9361\_adc\_sub application instance. \\
			\hline
			Property & \verb+LO_source+ &Enum& -        & -        & Readable, Writable, WriteSync & internal, external  & internal & The value 'external' should only be used if an external-to-the-FMCOMMS2/3 clock drives the TP102 test point on the FMCOMMS2/3 PCB. \\
			\hline
		\end{longtable}
	\end{scriptsize}

	Table \hypertarget{tab1}{1}: Structure declaration for \comp{}.rcc config property type.
	\begin{scriptsize}
		\begin{longtable}{|p{1.8cm}|p{3.6cm}|c|c|c|p{2cm}|p{3.7cm}|p{3.7cm}|p{2.5cm}|}
			\hline
			\rowcolor{blue}
			Type         & Name                                & Type & Sequence & Array      & Accessibility/ & Valid Range  & Default & Usage                                                                                                                                                                                                                       \\
			\rowcolor{blue}
			             &                                     &      & Length   & Dimensions & Advanced       &              &         &                                                                                                                                                                                                                             \\
			\hline
			Property     & \verb+reference_clk_rate_Hz+                   & Double & -        & -          & - & Standard & - & Schematic crystal Y101 frequency. \\
			\hline
			Property     & \verb+duplex_mode+                             & Enum   & -        & -          & - & TDD, FDD & - & - \\
			\hline
			Property     & \verb+are_using_REF_CLK_SMA+                             & Boolean& -        & -          & - & Standard & - & - \\
			\hline
			Property     & \verb+SMA_channel+                                       & Enum   & -        & -          & - & TX1A, TX2A & - & Indicates which SMA connector on the FMCOMMS2/3 PCB that the TX data stream controlled by an instance of this worker corresponds to. \\
			\hline
		\end{longtable}
	\end{scriptsize}

\end{landscape}

\section*{Performance and Resource Utilization}
\subsubsection*{fmcomms\_2\_3\_tx.rcc}
\begin{scriptsize}
	\begin{tabular}{|c|c|c|}
		\hline
		\rowcolor{blue}
		Processor Type & Processor Frequency & Run Function Time \\
		\hline
		TBD            & TBD                 & TBD               \\
		\hline
	\end{tabular}
\end{scriptsize}

\section*{Test and Verification}
No unit test for this worker exists. However, a hardware-in-the-loop application (which is NOT a unit test) exists for testing purposes (see applications/fmcomms\_2\_3\_tx\_test).

 \begin{thebibliography}{1}


 \bibitem{adi_ug570} AD9361 Reference Manual UG-570\\
 AD9361\_Reference\_Manual\_UG-570.pdf
 \end{thebibliography}
\end{document}
