\iffalse
This file is protected by Copyright. Please refer to the COPYRIGHT file
distributed with this source distribution.

This file is part of OpenCPI <http://www.opencpi.org>

OpenCPI is free software: you can redistribute it and/or modify it under the
terms of the GNU Lesser General Public License as published by the Free Software
Foundation, either version 3 of the License, or (at your option) any later
version.

OpenCPI is distributed in the hope that it will be useful, but WITHOUT ANY
WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A
PARTICULAR PURPOSE. See the GNU Lesser General Public License for more details.

You should have received a copy of the GNU Lesser General Public License along
with this program. If not, see <http://www.gnu.org/licenses/>.
\fi

\iffalse

This snippet creates a box labeled 'warning:backpressure' based on inputs.

Call it in two ways:

\backpressure{worker}{} % note the empty required second parameter!

or

\backpressure{worker1}{and ``worker2''}
or
\backpressure{worker1}{, ``worker2'', and ``worker3''}
etc.

\fi

\providecommand{\backpressure}[2]{
\label{warning:backpressure}
\begin{center}
\framebox{\parbox{0.8\linewidth}{\centering
  \ifthenelse{\equal{#2}{}}{The worker ``#1''}{The workers ``#1''#2} that implement\ifthenelse{\equal{#2}{}}{s}{} this component specification \ifthenelse{\equal{#2}{}}{is}{are} known to currently be faulty. \ifthenelse{\equal{#2}{}}{It}{They} do\ifthenelse{\equal{#2}{}}{es}{} not properly implement flow control (``backpressure'') and should be used with caution.
}}
\end{center}
}
