%TODO: Use LaTeX_Header
\documentclass{article}
\iffalse
This file is protected by Copyright. Please refer to the COPYRIGHT file
distributed with this source distribution.

This file is part of OpenCPI <http://www.opencpi.org>

OpenCPI is free software: you can redistribute it and/or modify it under the
terms of the GNU Lesser General Public License as published by the Free Software
Foundation, either version 3 of the License, or (at your option) any later
version.

OpenCPI is distributed in the hope that it will be useful, but WITHOUT ANY
WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A
PARTICULAR PURPOSE. See the GNU Lesser General Public License for more details.

You should have received a copy of the GNU Lesser General Public License along
with this program. If not, see <http://www.gnu.org/licenses/>.
\fi

% TODO: Version numbers?
\usepackage{graphicx}
\graphicspath{ {figures/} }
\usepackage{fancyhdr}
\usepackage{colortbl}
\usepackage[margin=.75in]{geometry}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage{footnote}
\pagestyle{fancy}
\lhead{Board Support Package Documentation}
\rhead{ANGRYVIPER Team}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\shellcmd}[1]{\texttt{\$ #1\\}}
\newcommand{\terminaloutput}[1]{\texttt{#1}}
\definecolor{blue}{rgb}{.5,1,1}
\definecolor{drkgreen}{rgb}{0,.6,0}
\def\snippetpath{../../../../../../doc/av/tex/snippets}
\input{\snippetpath/includes}
\usepackage{ifthen}

\begin{document}
\section*{ML605 Getting Started Guide}
\setcounter{section}{0}
\section{Hardware Prerequisites}
This section describes the hardware prerequisites required for an operational Xilinx Virtex-6 ML605 platform using OpenCPI. Note that the slot configurations in Table \ref{table:supported_slots} are limited by what FPGA bitstreams are currently built by OpenCPI and not by what hardware configurations are theoretically possible using OpenCPI.\\ \\
Hardware prerequisites are as follows.
\begin{itemize}
\item An ML605 board, which has undergone an OpenCPI-specific initial one-time hardware setup \cite{ml605_hardware_setup} and is plugged into a PCIE slot of an x86 computer.
\item Optionally, one of the following FMC card configurations in Table  \ref{table:supported_slots} may exist
\end{itemize}

\begin{center}
        \begin{table}[!htbp]
        \centering
        \caption{OpenCPI-supported ML605 hardware FMC slot configurations}
        \label{table:supported_slots}
        \begin{tabular}{|c|c|c|}
                \cline{2-3} \hline
                 & FMC LPC slot & FMC HPC slot \\ \hline
                \multicolumn{1}{|c|}{Zipper LPC setup\ref{deprecation_zipper}} & Modified\cite{zipper_mods} Zipper/MyriadRF & (empty)\\
                \multicolumn{1}{|c|}{ } & transceiver card & \\ \hline
                \multicolumn{1}{|c|}{Zipper HPC setup\ref{deprecation_zipper}} & (empty) & Modified\cite{zipper_mods} Zipper/MyriadRF \\
                \multicolumn{1}{|c|}{ } & & transceiver card \\ \hline
                \multicolumn{1}{|c|}{FMCOMMS2 LPC setup} & FMCOMMS2 & (empty)\\
                \multicolumn{1}{|c|}{ } & transceiver card & \\ \hline
                \multicolumn{1}{|c|}{FMCOMMS2 HPC setup (RX data flow only)} & (empty) & FMCOMMS2 \\
                \multicolumn{1}{|c|}{ } & & transceiver card \\ \hline
                \multicolumn{1}{|c|}{FMCOMMS3 LPC setup} & FMCOMMS3 & (empty)\\
                \multicolumn{1}{|c|}{ } & transceiver card & \\ \hline
                \multicolumn{1}{|c|}{FMCOMMS3 HPC setup (RX data flow only)} & (empty) & FMCOMMS3 \\
                \multicolumn{1}{|c|}{ } & & transceiver card \\ \hline
        \end{tabular}
        \end{table}
        \footnotetext[1]{\label{deprecation_zipper}Deprecated Support as
        of OpenCPI 1.5}


%       \footnotetext[1]{\label{nonspecprop}indicates a non-spec property, i.e. one declared in the OWD}

%\textsuperscript{\ref{deprecation_zipper}},

\end{center}

\section{Software Prerequisites}
\begin{itemize}
\item A CentOS 6 or CentOS 7 operating system installed on the x86 computer.
\item Xilinx ISE installed on the x86 computer, including the necessary Xilinx cable driver modifications necessary for CentOS. For information on supported ISE versions and cable driver modifications, refer to \cite{fpga_vendor_tool_guide}.
\item OpenCPI RPMs installed on the x86 computer. For more information refer to \cite{rpm_installation_guide}.
\item OpenCPI core project compiled for ml605.
\item OpenCPI assets project compiled for ml605.
\end{itemize}

\input{memmap}

\section{Driver Notes}
\input{Driver_Snippet}

\section{Loading the OpenCPI driver}
When OpenCPI is installed via RPMs, the OpenCPI driver should have been installed. However, when developing with source OpenCPI, the user is required to manage the loading of the OpenCPI driver. \\
The following terminal outputs are intended to provide the user with expected behavior of when the driver is not and is loaded. The user should note that only when the driver is installed can the ml605 be discovered as a valid OpenCPI container.

\begin{lstlisting}
ocpidriver unload
The driver module was successfully unloaded.

ocpidriver load
Found generic reserved DMA memory on the linux boot command line and assuming it is for OpenCPI: [memmap=128M$0x1000000]
Driver loaded successfully.

ocpidriver unload
The driver module was successfully unloaded.

ocpirun -C
OCPI( 2:816.0497): When searching for PCI device '0000:03:00.0': Can't open /dev/mem, forgot to load the driver? sudo?
OCPI( 2:816.0499): When searching for PCI device '0000:08:00.0': Can't open /dev/mem, forgot to load the driver? sudo?
OCPI( 2:816.0544): In HDL Container driver, got PCI search error: Can't open /dev/mem, forgot to load the driver? sudo?
Available containers:
 #  Model Platform       OS     OS-Version  Arch     Name
 0  rcc   centos7        linux  c7          x86_64   rcc0

ocpidriver load
Found generic reserved DMA memory on the linux boot command line and assuming it is for OpenCPI: [memmap=128M$0x1000000]
Driver loaded successfully.

ocpirun -C
Available containers:
 #  Model Platform       OS     OS-Version  Arch     Name
 0  hdl   ml605                                      PCI:0000:08:00.0
 1  hdl   alst4                                      PCI:0000:03:00.0
 2  rcc   centos7        linux  c7          x86_64   rcc0
\end{lstlisting}


\section{Proof of Operation}
The following commands may be run in order to verify correct OpenCPI operation on the x86/ML605 system.\\ \\
Existence of ML605 RCC/HDL containers may be verified by running the following command and verifying that similar output is produced.
\lstset{language=bash, backgroundcolor=\color{lightgray}, columns=flexible, breaklines=true, prebreak=\textbackslash, basicstyle=\ttfamily, showstringspaces=false,upquote=true, aboveskip=\baselineskip, belowskip=\baselineskip}
\begin{lstlisting}
ocpirun -C
Available containers:
 #  Model Platform       OS     OS-Version  Arch     Name
 0  hdl   ml605                                      PCI:0000:02:00.0
 1  rcc   centos7        linux  c7          x86_64   rcc0
\end{lstlisting}
Operation of the RCC container can be verified by running the hello application via the following command and verifying that identical output is produced. Note that the OCPI\_LIBRARY\_PATH environment variable must be setup to include the hello\_world.rcc built shared object file prior to running this command.
\begin{lstlisting}
ocpirun -t 1 assets/applications/hello.xml
Hello, world
\end{lstlisting}
Simultaneous RCC/HDL container operation can be verified by running the testbias application via the following command and verifying that identical output is produced. Note that the OCPI\_LIBRARY\_PATH environment variable must be setup correctly for your system prior to running this command.
\begin{lstlisting}
ocpirun -d -m bias=hdl assets/applications/testbias.xml
Property  0: file_read.fileName = "test.input" (cached)
Property  1: file_read.messagesInFile = "false" (cached)
Property  2: file_read.opcode = "0" (cached)
Property  3: file_read.messageSize = "16"
Property  4: file_read.granularity = "4" (cached)
Property  5: file_read.repeat = "<unreadable>"
Property  6: file_read.bytesRead = "0"
Property  7: file_read.messagesWritten = "0"
Property  8: file_read.suppressEOF = "false"
Property  9: file_read.badMessage = "false"
Property 10: file_read.ocpi_debug = "false" (parameter)
Property 11: file_read.ocpi_endian = "little" (parameter)
Property 12: bias.biasValue = "16909060" (cached)
Property 13: bias.ocpi_debug = "false" (parameter)
Property 14: bias.ocpi_endian = "little" (parameter)
Property 15: bias.test64 = "0"
Property 16: file_write.fileName = "test.output" (cached)
Property 17: file_write.messagesInFile = "false" (cached)
Property 18: file_write.bytesWritten = "0"
Property 19: file_write.messagesWritten = "0"
Property 20: file_write.stopOnEOF = "true" (cached)
Property 21: file_write.ocpi_debug = "false" (parameter)
Property 22: file_write.ocpi_endian = "little" (parameter)
Property  3: file_read.messageSize = "16"
Property  5: file_read.repeat = "<unreadable>"
Property  6: file_read.bytesRead = "4000"
Property  7: file_read.messagesWritten = "251"
Property  8: file_read.suppressEOF = "false"
Property  9: file_read.badMessage = "false"
Property 15: bias.test64 = "0"
Property 18: file_write.bytesWritten = "4000"
Property 19: file_write.messagesWritten = "250"
\end{lstlisting}

\section{Known Issues}
\subsection{Single Port of Data from CPU to FPGA} % AV-3783
\label{bug:3783}
The current implementations of the PCI-e specification on this platform correctly implements data flow from the CPU to the FPGA, only under certain configurations (assembly/container) and is limited to only a single port of data from CPU to FPGA. Fundamentally, OpenCPI only supports a single port connection from the CPU to the FPGA. \\ \\
To ensure the proper configurations are met, assembly and container XML files must be designed based on the following rules:
\begin{enumerate}
\item When a single worker exists in an assembly and it ports are connected to the assembly (Externals='true'), then
the container must be built for the "base" container. (i.e. the assembly's Makefile must contain "DefaultContainer=").
\item When an assembly's external connections are explicitly defined (i.e. not using Externals='true'), then the first external assembly connection that is defined in the assembly XML must be that of the CPU to FPGA, and the "base" container used (i.e. the assembly's Makefile must contain "DefaultContainer="), or
\item When defining external connections in a container XML, then the first interconnect container connection defined must be that of the CPU to FPGA and the "base" container used (i.e. the assembly's Makefile must contain "DefaultContainer=").
\end{enumerate}
Note that this applies to the TX/DAC data path connections for bitstreams with transceiver transmit data flow from a CPU (e.g. RCC worker to FPGA TX/DAC data path). See \path{projects/assets/hdl/assemblies/empty/cnt_1rx_1tx_bypassasm_fmcomms_2_3_lpc_LVDS_ml605.xml} as an example.

\pagebreak
  \begin{thebibliography}{1}

  \bibitem{ml605_hardware_setup}
	 \githubio[ML605 Hardware Setup]{assets/ML605\_Hardware\_Setup.pdf}
   \bibitem{fpga_vendor_tool_guide}
 	 \githubio[FPGA Vendor Tools Guide]{FPGA\_Vendor\_Tools\_Installation\_Guide.pdf}
 	   \bibitem{rpm_installation_guide}
 	 \githubio[OpenCPI RPM Installation Guide]{RPM\_Installation\_Guide.pdf}
 	   \bibitem{zipper_mods}
 	 \githubio[Required Modifications for Myriad-RF 1 and Zipper Daughtercards]{assets/Required\_Modifications\_for\_Myriad-RF\_1\_Zipper\_Daughtercards.pdf}
  \end{thebibliography}

\end{document}
